### 2019-07-29 paper/example_paper.tex
upload project to git

%%%%%%%% ICML 2019 EXAMPLE LATEX SUBMISSION FILE %%%%%%%%%%%%%%%%%

\documentclass{article}

% Recommended, but optional, packages for figures and better typesetting:
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{booktabs} % for professional tables

% hyperref makes hyperlinks in the resulting PDF.
% If your build breaks (sometimes temporarily if a hyperlink spans a page)
% please comment out the following usepackage line and replace
% \usepackage{icml2019} with \usepackage[nohyperref]{icml2019} above.
\usepackage{hyperref}

% Attempt to make hyperref and algorithmic work together better:
\newcommand{\theHalgorithm}{\arabic{algorithm}}

% Use the following line for the initial blind version submitted for review:
\usepackage[accepted]{icml2019}

% If accepted, instead use the following line for the camera-ready submission:
%\usepackage[accepted]{icml2019}

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{Submission and Formatting Instructions for ICML 2019}

\begin{document}

\twocolumn[
\icmltitle{Extending BERT for multi-choice problems \\}

% It is OKAY to include author information, even for blind
% submissions: the style file will automatically remove it for you
% unless you've provided the [accepted] option to the icml2019
% package.

% List of affiliations: The first argument should be a (short)
% identifier you will use later to specify author affiliations
% Academic affiliations should list Department, University, City, Region, Country
% Industry affiliations should list Company, City, Region, Country

% You can specify symbols, otherwise they are numbered in order.
% Ideally, you should not use this facility. Affiliations will be numbered
% in order of appearance and this is the preferred way.
\icmlsetsymbol{equal}{*}

\begin{icmlauthorlist}
\icmlauthor{Or Dremer}{equal,cs}
\icmlauthor{Afek Adler}{equal,in}
\end{icmlauthorlist}

\icmlaffiliation{in}{Department of Industrial Engineering, University of Tel Aviv, Tel Aviv, Israel}
\icmlaffiliation{cs}{Department of Computer Science, University of Tel Aviv, Tel Aviv, Israel.}

\icmlcorrespondingauthor{Afek Adler}{afekilayadler@gmail.com}
\icmlcorrespondingauthor{Or Dremer}{odermer@gmail.com}

% You may provide any keywords that you
% find helpful for describing your paper; these are used to populate
% the "keywords" metadata in the PDF but will not be shown in the document
\icmlkeywords{Machine Learning, NLP}

\vskip 0.3in
]

% this must go after the closing bracket ] following \twocolumn[ ...

% This command actually creates the footnote in the first column
% listing the affiliations and the copyright notice.
% The command takes one argument, which is text to display at the start of the footnote.
% The \icmlEqualContribution command is standard text for equal contribution.
% Remove it (just {}) if you do not need this facility.

%\printAffiliationsAndNotice{}  % leave blank if no need to mention equal contribution
\printAffiliationsAndNotice{\icmlEqualContribution} % otherwise use the standard text.

\begin{abstract}
Deep learning models are steal far away from human level performance in commonsense reasoning tasks.
We introduce a Question Answering scheme that models the dependencies between answers by
building a relationship graph between the answers for a given question. 
then, we compute a centrality measure for each node (answer) in the graph and predict the answer by taking the node with the maximum value of that centrality measure.
We test ourselves on the challenging CommonsenseQA dataset and show that although our method is capable of modeling more complex relationships between the answers we did not manage to improve the current state of the art.
\end{abstract}

\section{Introduction}
When we face a multi-choice problem where we have to choose the most 
probable answer we arrive to it with prior information and knowledge. for example, we have some kind of a
language model that tells us if sentence A is more probable then sentence B, and we have knowledge about the physical world which tells us what is more possible or probable.

Whereas in some cases we succeeded to build algorithms that are better then humans on many machine learning tasks from different disciplines (e.g computer vision and  natural language processing). In the field of common sense reasoning (reference to commonsenseqa) state of the art algorithms are steal inferior to human level performance - this methods mainly use massive datasets of labeled examples with supervised machine learning algorithms in order to infer prediction roles. but in cases such as learning common sense and problems such as learning negative facts it is likely that this knowledge does not exist in the corpus of the pretrained language model but only in the dataset which is fine-tuned .

due to this inherent difficulty of this methods the research community invested resources in creating a larger scale datasets specifically for common sense inference (swag,commonsenseqa,Explain Yourself!).

\section{Background and Related Work}
Submission cite{TechReport} to ICML 2019 will be entirely electronic, via a web site
(not email). Information about the submission process and \LaTeX\ templates
are available on the conference web site at:
\begin{center}
\textbf{\texttt{http://icml.cc/}}
\end{center}

The guidelines below will be enforced for initial submissions and
camera-ready copies. Here is a brief summary:
\begin{itemize}
\item Submissions must be in PDF\@.
\item Submitted papers can be up to eight pages long, not including references, and up to twelve pages when references and acknowledgments are included. Any paper exceeding this length will automatically be rejected. 
\item \textbf{Do not include author information or acknowledgements} in your
    initial submission.
\item Your paper should be in \textbf{10 point Times font}.
\item Make sure your PDF file only uses Type-1 fonts.
\item Place figure captions \emph{under} the figure (and omit titles from inside
    the graphic file itself). Place table captions \emph{over} the table.
\item References must include page numbers whenever possible and be as complete
    as possible. Place multiple citations in chronological order.
\item Do not alter the style template; in particular, do not compress the paper
    format by reducing the vertical spaces.
\item Keep your abstract brief and self-contained, one paragraph and roughly
    4--6 sentences. Gross violations will require correction at the
    camera-ready phase. The title should have content words capitalized.
\end{itemize}

\subsection{Submitting Papers}

\textbf{Paper Deadline:} The deadline for paper submission that is
advertised on the conference website is strict. If your full,
anonymized, submission does not reach us on time, it will not be
considered for publication.

\textbf{Anonymous Submission:} ICML uses double-blind review: no identifying
author information may appear on the title page or in the paper
itself. Section~\ref{author info} gives further details.

\textbf{Simultaneous Submission:} ICML will not accept any paper which,
at the time of submission, is under review for another conference or
has already been published. This policy also applies to papers that
overlap substantially in technical content with conference papers
under review or previously published. ICML submissions must not be
submitted to other conferences during ICML's review period. Authors
may submit to ICML substantially different versions of journal papers
that are currently under review by the journal, but not yet accepted
at the time of submission. Informal publications, such as technical
reports or papers in workshop proceedings which do not appear in
print, do not fall under these restrictions.

\medskip

Authors must provide their manuscripts in \textbf{PDF} format.
Furthermore, please make sure that files contain only embedded Type-1 fonts
(e.g.,~using the program \texttt{pdffonts} in linux or using
File/DocumentProperties/Fonts in Acrobat). Other fonts (like Type-3)
might come from graphics files imported into the document.

Authors using \textbf{Word} must convert their document to PDF\@. Most
of the latest versions of Word have the facility to do this
automatically. Submissions will not be accepted in Word format or any
format other than PDF\@. Really. We're not joking. Don't send Word.

Those who use \textbf{\LaTeX} should avoid including Type-3 fonts.
Those using \texttt{latex} and \texttt{dvips} may need the following
two commands:

{\footnotesize
\begin{verbatim}
dvips -Ppdf -tletter -G0 -o paper.ps paper.dvi
ps2pdf paper.ps
\end{verbatim}}
It is a zero following the ``-G'', which tells dvips to use
the config.pdf file. Newer \TeX\ distributions don't always need this
option.

Using \texttt{pdflatex} rather than \texttt{latex}, often gives better
results. This program avoids the Type-3 font problem, and supports more
advanced features in the \texttt{microtype} package.

\textbf{Graphics files} should be a reasonable size, and included from
an appropriate format. Use vector formats (.eps/.pdf) for plots,
lossless bitmap formats (.png) for raster graphics with sharp lines, and
jpeg for photo-like images.

The style file uses the \texttt{hyperref} package to make clickable
links in documents. If this causes problems for you, add
\texttt{nohyperref} as one of the options to the \texttt{icml2019}
usepackage statement.

\subsection{Submitting Final Camera-Ready Copy}

The final versions of papers accepted for publication should follow the
same format and naming convention as initial submissions, except that
author information (names and affiliations) should be given. See
Section~\ref{final author} for formatting instructions.

The footnote, ``Preliminary work. Under review by the International
Conference on Machine Learning (ICML). Do not distribute.'' must be
modified to ``\textit{Proceedings of the
$\mathit{36}^{th}$ International Conference on Machine Learning},
Long Beach, USA, 2019.
Copyright 2019 by the author(s).''

For those using the \textbf{\LaTeX} style file, this change (and others) is
handled automatically by simply changing
$\mathtt{\backslash usepackage\{icml2019\}}$ to
$$\mathtt{\backslash usepackage[accepted]\{icml2019\}}$$
Authors using \textbf{Word} must edit the
footnote on the first page of the document themselves.

Camera-ready copies should have the title of the paper as running head
on each page except the first one. The running title consists of a
single line centered above a horizontal rule which is $1$~point thick.
The running head should be centered, bold and in $9$~point type. The
rule should be $10$~points above the main text. For those using the
\textbf{\LaTeX} style file, the original title is automatically set as running
head using the \texttt{fancyhdr} package which is included in the ICML
2019 style file package. In case that the original title exceeds the
size restrictions, a shorter form can be supplied by using

\verb|\icmltitlerunning{...}|

just before $\mathtt{\backslash begin\{document\}}$.
Authors using \textbf{Word} must edit the header of the document themselves.

\section{Format of the Paper}

All submissions must follow the specified format.

\subsection{Length and Dimensions}

Submitted papers can be up to eight pages long, not including references, and up to twelve pages when references and acknowledgments are included.
Acknowledgements should be limited to grants and people who contributed to the paper.
Any submission that exceeds
this page limit, or that diverges significantly from the specified format,
will be rejected without review.

The text of the paper should be formatted in two columns, with an
overall width of 6.75~inches, height of 9.0~inches, and 0.25~inches
between the columns. The left margin should be 0.75~inches and the top
margin 1.0~inch (2.54~cm). The right and bottom margins will depend on
whether you print on US letter or A4 paper, but all final versions
must be produced for US letter size.

The paper body should be set in 10~point type with a vertical spacing
of 11~points. Please use Times typeface throughout the text.

\subsection{Title}

The paper title should be set in 14~point bold type and centered
between two horizontal rules that are 1~point thick, with 1.0~inch
between the top rule and the top edge of the page. Capitalize the
first letter of content words and put the rest of the title in lower
case.

\subsection{Author Information for Submission}
\label{author info}

ICML uses double-blind review, so author information must not appear. If
you are using \LaTeX\/ and the \texttt{icml2019.sty} file, use
\verb+\icmlauthor{...}+ to specify authors and \verb+\icmlaffiliation{...}+ to specify affiliations. (Read the TeX code used to produce this document for an example usage.) The author information
will not be printed unless \texttt{accepted} is passed as an argument to the
style file.
Submissions that include the author information will not
be reviewed.

\subsubsection{Self-Citations}

If you are citing published papers for which you are an author, refer
to yourself in the third person. In particular, do not use phrases
that reveal your identity (e.g., ``in previous work \cite{langley00}, we
have shown \ldots'').

Do not anonymize citations in the reference section. The only exception are manuscripts that are
not yet published (e.g., under submission). If you choose to refer to
such unpublished manuscripts \cite{anonymous}, anonymized copies have
to be submitted
as Supplementary Material via CMT\@. However, keep in mind that an ICML
paper should be self contained and should contain sufficient detail
for the reviewers to evaluate the work. In particular, reviewers are
not required to look at the Supplementary Material when writing their
review.

\subsubsection{Camera-Ready Author Information}
\label{final author}

If a paper is accepted, a final camera-ready copy must be prepared.
%
For camera-ready papers, author information should start 0.3~inches below the
bottom rule surrounding the title. The authors' names should appear in 10~point
bold type, in a row, separated by white space, and centered. Author names should
not be broken across lines. Unbolded superscripted numbers, starting 1, should
be used to refer to affiliations.

Affiliations should be numbered in the order of appearance. A single footnote
block of text should be used to list all the affiliations. (Academic
affiliations should list Department, University, City, State/Region, Country.
Similarly for industrial affiliations.)

Each distinct affiliations should be listed once. If an author has multiple
affiliations, multiple superscripts should be placed after the name, separated
by thin spaces. If the authors would like to highlight equal contribution by
multiple first authors, those authors should have an asterisk placed after their
name in superscript, and the term ``\textsuperscript{*}Equal contribution"
should be placed in the footnote block ahead of the list of affiliations. A
list of corresponding authors and their emails (in the format Full Name
\textless{}email@domain.com\textgreater{}) can follow the list of affiliations.
Ideally only one or two names should be listed.

A sample file with author names is included in the ICML2019 style file
package. Turn on the \texttt{[accepted]} option to the stylefile to
see the names rendered. All of the guidelines above are implemented
by the \LaTeX\ style file.

\subsection{Abstract}

The paper abstract should begin in the left column, 0.4~inches below the final
address. The heading `Abstract' should be centered, bold, and in 11~point type.
The abstract body should use 10~point type, with a vertical spacing of
11~points, and should be indented 0.25~inches more than normal on left-hand and
right-hand margins. Insert 0.4~inches of blank space after the body. Keep your
abstract brief and self-contained, limiting it to one paragraph and roughly 4--6
sentences. Gross violations will require correction at the camera-ready phase.

\subsection{Partitioning the Text}

You should organize your paper into sections and paragraphs to help
readers place a structure on the material and understand its
contributions.

\subsubsection{Sections and Subsections}

Section headings should be numbered, flush left, and set in 11~pt bold
type with the content words capitalized. Leave 0.25~inches of space
before the heading and 0.15~inches after the heading.

Similarly, subsection headings should be numbered, flush left, and set
in 10~pt bold type with the content words capitalized. Leave
0.2~inches of space before the heading and 0.13~inches afterward.

Finally, subsubsection headings should be numbered, flush left, and
set in 10~pt small caps with the content words capitalized. Leave
0.18~inches of space before the heading and 0.1~inches after the
heading.

Please use no more than three levels of headings.

\subsubsection{Paragraphs and Footnotes}

Within each section or subsection, you should further partition the
paper into paragraphs. Do not indent the first line of a given
paragraph, but insert a blank line between succeeding ones.

You can use footnotes\footnote{Footnotes
should be complete sentences.} to provide readers with additional
information about a topic without interrupting the flow of the paper.
Indicate footnotes with a number in the text where the point is most
relevant. Place the footnote in 9~point type at the bottom of the
column in which it appears. Precede the first footnote in a column
with a horizontal rule of 0.8~inches.\footnote{Multiple footnotes can
appear in each column, in the same order as they appear in the text,
but spread them across columns and pages if possible.}

\begin{figure}[ht]
\vskip 0.2in
\begin{center}
\centerline{\includegraphics[width=\columnwidth]{icml_numpapers}}
\caption{Historical locations and number of accepted papers for International
Machine Learning Conferences (ICML 1993 -- ICML 2008) and International
Workshops on Machine Learning (ML 1988 -- ML 1992). At the time this figure was
produced, the number of accepted papers for ICML 2008 was unknown and instead
estimated.}
\label{icml-historical}
\end{center}
\vskip -0.2in
\end{figure}

\subsection{Figures}

You may want to include figures in the paper to illustrate
your approach and results. Such artwork should be centered,
legible, and separated from the text. Lines should be dark and at
least 0.5~points thick for purposes of reproduction, and text should
not appear on a gray background.

Label all distinct components of each figure. If the figure takes the
form of a graph, then give a name for each axis and include a legend
that briefly describes each curve. Do not include a title inside the
figure; instead, the caption should serve this function.

Number figures sequentially, placing the figure number and caption
\emph{after} the graphics, with at least 0.1~inches of space before
the caption and 0.1~inches after it, as in
Figure~\ref{icml-historical}. The figure caption should be set in
9~point type and centered unless it runs two or more lines, in which
case it should be flush left. You may float figures to the top or
bottom of a column, and you may set wide figures across both columns
(use the environment \texttt{figure*} in \LaTeX). Always place
two-column figures at the top or bottom of the page.

\subsection{Algorithms}

If you are using \LaTeX, please use the ``algorithm'' and ``algorithmic''
environments to format pseudocode. These require
the corresponding stylefiles, algorithm.sty and
algorithmic.sty, which are supplied with this package.
Algorithm~\ref{alg:example} shows an example.

\begin{algorithm}[tb]
   \caption{Bubble Sort}
   \label{alg:example}
\begin{algorithmic}
   \STATE {\bfseries Input:} data $x_i$, size $m$
   \REPEAT
   \STATE Initialize $noChange = true$.
   \FOR{$i=1$ {\bfseries to} $m-1$}
   \IF{$x_i > x_{i+1}$}
   \STATE Swap $x_i$ and $x_{i+1}$
   \STATE $noChange = false$
   \ENDIF
   \ENDFOR
   \UNTIL{$noChange$ is $true$}
\end{algorithmic}
\end{algorithm}

\subsection{Tables}

You may also want to include tables that summarize material. Like
figures, these should be centered, legible, and numbered consecutively.
However, place the title \emph{above} the table with at least
0.1~inches of space before the title and the same after it, as in
Table~\ref{sample-table}. The table title should be set in 9~point
type and centered unless it runs two or more lines, in which case it
should be flush left.

% Note use of \abovespace and \belowspace to get reasonable spacing
% above and below tabular lines.

\begin{table}[t]
\caption{Classification accuracies for naive Bayes and flexible
Bayes on various data sets.}
\label{sample-table}
\vskip 0.15in
\begin{center}
\begin{small}
\begin{sc}
\begin{tabular}{lcccr}
\toprule
Data set & Naive & Flexible & Better? \\
\midrule
Breast    & 95.9$\pm$ 0.2& 96.7$\pm$ 0.2& $\surd$ \\
Cleveland & 83.3$\pm$ 0.6& 80.0$\pm$ 0.6& $\times$\\
Glass2    & 61.9$\pm$ 1.4& 83.8$\pm$ 0.7& $\surd$ \\
Credit    & 74.8$\pm$ 0.5& 78.3$\pm$ 0.6&         \\
Horse     & 73.3$\pm$ 0.9& 69.7$\pm$ 1.0& $\times$\\
Meta      & 67.1$\pm$ 0.6& 76.5$\pm$ 0.5& $\surd$ \\
Pima      & 75.1$\pm$ 0.6& 73.9$\pm$ 0.5&         \\
Vehicle   & 44.9$\pm$ 0.6& 61.5$\pm$ 0.4& $\surd$ \\
\bottomrule
\end{tabular}
\end{sc}
\end{small}
\end{center}
\vskip -0.1in
\end{table}

Tables contain textual material, whereas figures contain graphical material.
Specify the contents of each row and column in the table's topmost
row. Again, you may float tables to a column's top or bottom, and set
wide tables across both columns. Place two-column tables at the
top or bottom of the page.

\subsection{Citations and References}

Please use APA reference format regardless of your formatter
or word processor. If you rely on the \LaTeX\/ bibliographic
facility, use \texttt{natbib.sty} and \texttt{icml2019.bst}
included in the style-file package to obtain this format.

Citations within the text should include the authors' last names and
year. If the authors' names are included in the sentence, place only
the year in parentheses, for example when referencing Arthur Samuel's
pioneering work \yrcite{Samuel59}. Otherwise place the entire
reference in parentheses with the authors and year separated by a
comma \cite{Samuel59}. List multiple references separated by
semicolons \cite{kearns89,Samuel59,mitchell80}. Use the `et~al.'
construct only for citations with three or more authors or after
listing all authors to a publication in an earlier reference \cite{MachineLearningI}.

Authors should cite their own work in the third person
in the initial version of their paper submitted for blind review.
Please refer to Section~\ref{author info} for detailed instructions on how to
cite your own papers.

Use an unnumbered first-level section heading for the references, and use a
hanging indent style, with the first line of the reference flush against the
left margin and subsequent lines indented by 10 points. The references at the
end of this document give examples for journal articles \cite{Samuel59},
conference publications \cite{langley00}, book chapters \cite{Newell81}, books
\cite{DudaHart2nd}, edited volumes \cite{MachineLearningI}, technical reports
\cite{mitchell80}, and dissertations \cite{kearns89}.

Alphabetize references by the surnames of the first authors, with
single author entries preceding multiple author entries. Order
references for the same authors by year of publication, with the
earliest first. Make sure that each reference includes all relevant
information (e.g., page numbers).

Please put some effort into making references complete, presentable, and
consistent. If using bibtex, please protect capital letters of names and
abbreviations in titles, for example, use \{B\}ayesian or \{L\}ipschitz
in your .bib file.

\subsection{Software and Data}

We strongly encourage the publication of software and data with the
camera-ready version of the paper whenever appropriate. This can be
done by including a URL in the camera-ready copy. However, do not
include URLs that reveal your institution or identity in your
submission for review. Instead, provide an anonymous URL or upload
the material as ``Supplementary Material'' into the CMT reviewing
system. Note that reviewers are not required to look at this material
when writing their review.

% Acknowledgements should only appear in the accepted version.
\section*{Acknowledgements}

\textbf{Do not} include acknowledgements in the initial version of
the paper submitted for blind review.

If a paper is accepted, the final camera-ready version can (and
probably should) include acknowledgements. In this case, please
place such acknowledgements in an unnumbered section at the
end of the paper. Typically, this will include thanks to reviewers
who gave useful comments, to colleagues who contributed to the ideas,
and to funding agencies and corporate sponsors that provided financial
support.

% In the unusual situation where you want a paper to appear in the
% references without citing it in the main text, use \nocite
\nocite{langley00}

\bibliography{example_paper}
\bibliographystyle{icml2019}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% DELETE THIS PART. DO NOT PLACE CONTENT AFTER THE REFERENCES!
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix
\section{Do \emph{not} have an appendix here}

\textbf{\emph{Do not put content after the references.}}
%
Put anything that you might normally include after the references in a separate
supplementary file.

We recommend that you build supplementary material in a separate document.
If you must create one PDF and cut it up, please be careful to use a tool that
doesn't alter the margins, and that doesn't aggressively rewrite the PDF file.
pdftk usually works fine.

\textbf{Please do not use Apple's preview to cut off supplementary material.} In
previous years it has altered margins, and created headaches at the camera-ready
stage. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

% This document was modified from the file originally made available by
% Pat Langley and Andrea Danyluk for ICML-2K. This version was created
% by Iain Murray in 2018, and modified by Alexandre Bouchard in
% 2019. Previous contributors include Dan Roy, Lise Getoor and Tobias
% Scheffer, which was slightly modified from the 2010 version by
% Thorsten Joachims & Johannes Fuernkranz, slightly modified from the
% 2009 version by Kiri Wagstaff and Sam Roweis's 2008 version, which is
% slightly modified from Prasad Tadepalli's 2007 version which is a
% lightly changed version of the previous year's version by Andrew
% Moore, which was in turn edited from those of Kristian Kersting and
% Codrina Lauth. Alex Smola contributed to the algorithmic style files.

### 2019-07-31 paper/example_paper.tex
added  background and related work

@@
 \usepackage[accepted]{icml2019}
-
+% \usepackage[style=authoryear]{biblatex}
+% \addbibresource{example_paper.bib}
 % If accepted, instead use the following line for the camera-ready submission:
@@
 \begin{icmlauthorlist}
-\icmlauthor{Or Dremer}{equal,cs}
+\icmlauthor{Orr Dermer}{equal,cs}
 \icmlauthor{Afek Adler}{equal,in}
@@
 \icmlcorrespondingauthor{Afek Adler}{afekilayadler@gmail.com}
-\icmlcorrespondingauthor{Or Dremer}{odermer@gmail.com}
+\icmlcorrespondingauthor{Orr Dermer}{odermer@gmail.com}
 
@@
 \begin{abstract}
-Deep learning models are steal far away from human level performance in commonsense reasoning tasks.
-We introduce a Question Answering scheme that models the dependencies between answers by
+Deep learning models are still far away from human-level performance in commonsense reasoning tasks.
+We introduce a multi-choice question answering scheme that models the dependencies between answers by
 building a relationship graph between the answers for a given question. 
 then, we compute a centrality measure for each node (answer) in the graph and predict the answer by taking the node with the maximum value of that centrality measure.
-We test ourselves on the challenging CommonsenseQA dataset and show that although our method is capable of modeling more complex relationships between the answers we did not manage to improve the current state of the art.
+We test ourselves on the challenging CommonsenseQA dataset and show that although our method is capable of modeling more complex relationships between the answers we did not manage to improve the current state of the art on this task.
 \end{abstract}
@@
 \section{Introduction}
-When we face a multi-choice problem where we have to choose the most 
-probable answer we arrive to it with prior information and knowledge. for example, we have some kind of a
-language model that tells us if sentence A is more probable then sentence B, and we have knowledge about the physical world which tells us what is more possible or probable.
+When we face a multi-choice question answering (QA) problem where we have to choose the most 
+probable answer we arrive at it with prior information and knowledge. for instance, we have some kind of a
 
-Whereas in some cases we succeeded to build algorithms that are better then humans on many machine learning tasks from different disciplines (e.g computer vision and  natural language processing).
-In the field of common sense reasoning (reference to commonsenseqa) state of the art algorithms are steal inferior to human level performance - this methods mainly use massive datasets of labeled examples with supervised machine learning algorithms in order to infer prediction roles.
-but in cases such as learning common sense and problems such as learning negative facts it is likely that this knowledge does not exist in the corpus of the pretrained language model but only in the dataset which is fine-tuned .
+Whereas in some cases the state of the art machine-learning methods which were trained on massive amount of data to infer prediction roles
+outperforms human-level by a large margin (e.g. SQUAD 2.0 \cite{rajpurkar2018know}),
+In the field of common sense reasoning  \cite{talmor2018commonsenseqa} state of the art algorithms fail to generalize and are yet inferior to human level performance.
+this is due to two main reasons.
+first, is that when using algorithms such as fine-tuning a pre-trained language model, it is likely that this knowledge (common sense) does not exist explicitly in the pre training corpus.
+and second, is due to the fact that creating massive datasets for this purpose solely is hard, and developed only in the last years mostly by crowdsourcing.
 
-due to this inherent difficulty of this methods the research community invested resources in creating a larger scale datasets specifically for common sense inference (swag,commonsenseqa,Explain Yourself!).
+Due to this inherent difficulty of this methods the research community invests resources in creating larger-scale datasets in different difficulty levels, e.g., the SWAG \cite{zellers2018swag} dataset with ~100K examples where \cite{devlin2018bert} demonstrate a model which is already at a human level and the CommonseneQA \cite{talmor2018commonsenseqa} a dataset which was made especially for common sense reasoning with \~{}10K samples where the state of the art is much lower then human-level.
+for a detailed survey of resources see \cite{storks2019commonsense}.
+
+In this work, we suggest and evaluate models which eliminate the Independence assumption between answers for a given question, aiming to improve the benchmark on the CommonsenseQA dataset.
 
 \section{Background and Related Work}
+Research on machine common sense QA has long been acknowledged for it's critical component in natural language understanding.
+but only recently with the embracing of deep learning in natural language processing and crowdsourcing to create larger scale datasets, major breakthroughs has emerged; to the best of the author's knowledge, the first large scale common sense reasoning QA dataset was introduced is 2018 \cite{storks2019commonsense}.
+
+Due to the fact that the prominent approach to to solve common sense QA problems is with word embeddings (WE) and contextualized word embeddings (CWE) in the next section we will provide a brief introduction to CVE and explain how to use it in the context of common sense QA.
+
+% We would like to note that this paper address specifically solutions for multi-choice QA with common sense reasoning and not closely related themes such as visual commonsense reasoning or co reference resolution.
+
+\subsection{Contextualized Word Embeddings}
+Based on the pioneering work of Word2Vec \cite{mikolov2013distributed} which enabled words to be represented as vectors, those
+enriching the information contained in the input for a variation of language based machine learning tasks, many models extended the Word2Vec concept by taking context into account; the same word has a different meaning in different context.
+the leading approaches to obtain a contextualized word representations is using the hidden layer of an LSTM \cite{hochreiter1997long} and more specifically a biLSTM such as in ELMO \cite{peters2018deep} or more recently using a transformer architecture such as \cite{devlin2018bert,yang2019xlnet}.
+
+The great power of WE or CWE is to enable using a generic method as a basis for task specific machine learning models; for instance, in natural language processing there are many different tasks (e.g.
+machine translation, sentiment analysis) and a simple model based on CWE with fine tuning on a given dataset usually provides much better results than previous models on a given task, creating a new bencmark for this specific task.
+the fact that mega companies provides those trained models as an open source service makes it easy to use for academics and in the industry as one.
+
+CWE is a type of transfer learning method; a model is pretrained on a base dataset and fine tuned on the task dataset,  with the underlying hypothesis that information distilation is possible from one source (base dataset) to the other (task specific dataset).
+The main reason for the great success of CWE is that the base model is trained using supervised learning on huge amounts of data, e.g.
+BERT, was trained on 3,300M words.
+the fact that CWE models are also self trained makes it easier to collect such huge amount of data without the need to label examples.
+the downside of this models is that they use many parameters (BERT Large - 330M) - so trainig and infering requires large processing power and latency is a challenge for creating real time systems.
+in the next section we will introduce the benchmark model which we aim to improve - BERT for CommonsenseQA (which is identical to BERT for SWAG) as was introduced in the original paper of BERT.
+
+\subsection{BERT benchmark for SWAG}
+
 Submission cite{TechReport} to ICML 2019 will be entirely electronic, via a web site
@@
 
+% \printbibliography
 \end{document}

### 2019-08-01 paper/paper.tex
Started methodology section

--- 2019-07-31 paper/example_paper.tex
@@
 \subsection{BERT benchmark for SWAG}
+
+\section{Methodology}
+
+We derive our model from the BERT fine-tuning method over multichoice questions, as displayed in the original paper.
+However, as we want our model to compare between the different possible answers, we deviate from the original model by introducing the model with the question and 2 possible answers as each input sequence, for which the model returns a score - 1 meaning the first answer is more likely, and 0 if the second answer is the likeliest.
+Having received a score for each of pairs, we then integrate those into probability scores for each of the original answers - and then choose the one with the highest probability as our predicted answer.
+
+\subsection{Dataset alterations}
+
+In the original paper, each input sequence consisted of a classifier token ('[CLS]'), the question, a separator token ('[SEP]'), a possible answer, and then another separator token.
+The classifier token is unique, as the final hidden state corresponding to that token was used as the aggregate sequence representation for the question-answering task.
+Our model deviates from these assumptions.
+Instead, each input sequence was constructed from the question and 2 possible answers in the following manner: A classifier token, the first answer, a separator token, the question, a separator token, the second answer, and another classifier token.
+Note, that this construction break several of the original BERT paper assumptions - each of our input sequences consist of more than just one classifier token, and more than just two sentences.
+As such, it is possible that BERT will suffer from reduced performance, as its entire training process was built around these assumptions.
+However, breaking these assumptions was a crucial part of what made our constructions work - it allowed for each of the classifier tokens to "absorb" the meaning of the answer closer to it, and imporved the symmetry of our model in regard to each of the two answers.
+
+% TODO: add a diagram displaying our construct
+
+\section{Stuff from the example paper}
 

### 2019-08-01 paper/paper.tex
Input sequence segment embeddings

@@
 % TODO: add a diagram displaying our construct
+
+Another part of the input sequence given to BERT is the segment embeddings - a number from {0, 1} which signifies wether the current token is part of the first sentece or the second.
+After trial and error, it was found that we perform best when giving a value of 1 for \emph{each} of the answer tokens, and 0 for the question tokens.
+That makes sense, as part of the desire for symmetry in our model, and the fact that BERT wasn't trained with a possibilty for a third sentence, so using, for example, the number 2 for our second answer would not make any sense to it.
+
+\subsection{Pair scores integration}
 

### 2019-08-02 paper/paper.tex
Added pair scores integration

@@
 \usepackage{subfigure}
+\usepackage{amsmath}
 \usepackage{booktabs} % for professional tables
@@
 
-% TODO: add a diagram displaying our construct
+% TODO: add a diagram displaying our construct and the score calculation (including calculating for (i,j) and (j,i) and averaging with 1-s_(j,i)).
 
 Another part of the input sequence given to BERT is the segment embeddings - a number from {0, 1} which signifies wether the current token is part of the first sentece or the second.
-After trial and error, it was found that we perform best when giving a value of 1 for \emph{each} of the answer tokens, and 0 for the question tokens.
+After trial and error, it was found that we perform best when giving a value of 1 for \textbf{each} of the answer tokens, and 0 for the question tokens.
 That makes sense, as part of the desire for symmetry in our model, and the fact that BERT wasn't trained with a possibilty for a third sentence, so using, for example, the number 2 for our second answer would not make any sense to it.
 
+After passing our input sequence through BERT, we use a concatenation of the final hidden states matching the classifier tokens as the sequence representation.
+We also learn as a parameter a vector whose dot product with the sequence representation is the score for the given answer pair.
+
 \subsection{Pair scores integration}
+
+We conceived a few methods of combining the different pair scores into probabilities for the answers. In this section we will review those methods and compare them.
+
+\subsubsection{Learnt weights}
+
+In this method, we introduce more layers to derive the indiviual probabilities from the pair scores.
+We used 2 layers, with a hidden size of $ (number\ of\ pairs)^2 $ and normalizing with a softmax layer.
+
+\subsubsection{Markov chains}
+
+In this method, we find the stationary distribution of a weighted graph whose edge's weights are derived from our pair scores.
+The reasoning for this process is as follows - imagine a graph whose vertices are the given answers.
+We begin by choosing an answer randomly, and we want to move on to the best possible answer.
+At each time step, we move to a different answer, choosing based on the scores of the pairs in which our current answer participates, i.e.
+the better another answer performed against our current answer, the more likely we are to move to it.
+This process is powerful, because it captures the dependency between the different answers, e.g.
+if answer B is better than answer A, and answer C is better than answer B, than we'd like to factor in that information when comparing between answers A and C.
+
+Simply constructing a matrix with each cell being the score for the matching pair, normalizing each row so that we have a probability matrix, and then calculating the stationary distribution doesn't work well in practice.
+This is because normalizing the matrix causes the model to be unable to understand the absolute value of the scores, e.g.
+if it sees a row in which all values are similar, it can't differ the case in which all scores were low (and thus our "current" answer is good) from the case all of the scores were high.
+Consider the following matrix:
+
+$$
+\begin{bmatrix}
+0 & 0.95 & 0.85 & 0.25 \\
+0.05 & 0 & 0.98 & 0.74 \\
+0.15 & 0.02 & 0 & 0.45 \\
+0.75 & 0.26 & 0.55 & 0
+\end{bmatrix}
+$$
+
+We can see that the third answer had won in every comparison - thus, we would expect it to be assigned the highest probability.
+Given the currently described method, this in not the case, as the probabilities received would be:
+$$ \begin{bmatrix} 0.22614831 & 0.16630443 & 0.29576885 & \textbf{0.31177841} \end{bmatrix} $$
+
+We solve this problem by adding the average of each column to the matching cell on the diagonal.
+This makes sense, as this gives us the option of staying on the current choice, and the better a certain choice had performed against the other choices, the greater the possibilty of staying on it.
+After doing this, we derive this matrix for our example:
+
+$$
+\begin{bmatrix}
+\textbf{0.31} & 0.95 & 0.85 & 0.25 \\
+0.05 & \textbf{0.41} & 0.98 & 0.74 \\
+0.15 & 0.02 & \textbf{0.79} & 0.45 \\
+0.75 & 0.26 & 0.55 & \textbf{0.48}
+\end{bmatrix}
+$$
+
+And this probability matrix for our choices:
+$$ \begin{bmatrix} 0.16845236 & 0.13252954 & \textbf{0.43521662} & 0.26380148 \end{bmatrix} $$
+
+\subsection{Learning}
 

### 2019-08-02 paper/paper.tex
Tie-breakers

@@
 After passing our input sequence through BERT, we use a concatenation of the final hidden states matching the classifier tokens as the sequence representation.
-We also learn as a parameter a vector whose dot product with the sequence representation is the score for the given answer pair.
+We learn as a parameter a vector whose dot product with the sequence representation is the score for the given answer pair.
 
@@
 if answer B is better than answer A, and answer C is better than answer B, than we'd like to factor in that information when comparing between answers A and C.
+
+% TODO: add a markov chain graph here
 
@@
 
-\subsection{Learning}
+\subsubsection{Tie-breakers}
+
+This is not a method on its own, but it can be used on top of the other ones.
+Essentially, we can assert a "Certainty Threshold" on the probabilities obtained from the other methods, a rate between two probabilities under which we consider our prediction to be uncertain/unstable.
+If such a scenario arises, we then resort to choosing between the two highest-scored choices directly - that is, by looking at the score given to the pair and deciding accordingly.
+
+Note that this change does not cause a change in the probabilities themselves, it only changes the predicted answer.
+As such, it does not cause a change in the measured loss, thus does not affect the learned parameters.
+It does change, however, the measured accuracy, which means that when learning parameters we will favor a parameter set that maximizes the accuracy given this change.
+
+\section{Experiments and Results}
+
+As our model deviates greatly from the assumptions that were made when the original BERT weights were trained, it is understanable that our model required more epochs to converge than the amount of epochs the original paper used when fine-tuning to the question answering task.
+We should also note that because each sample now consists of much more input sequences (the original model had one sequence per possible answer, our model has one sequence per possible answer \textbf{pair}), we are now more limited in our batch size, as the GPU has to hold the entire batch simultaneously.
+This problem can be mitigated by using gradient accumulation.
+
+Our models were trained in parts.
+In the first part, we trained solely on the dataset alterations part, without intergrating the pair scores. That is, our model was trained directly on identifying the better answer in a pair
 

### 2019-08-03 paper/diagram.tex
Added original paper diagram

\documentclass{article}

\usepackage[latin1]{inputenc}
\usepackage{tikz}

\usetikzlibrary{shapes,arrows}

\begin{document}
\pagestyle{empty}

% Define block styles
\tikzstyle{decision} = [diamond, draw, fill=blue!20, 
    text width=4.5em, text badly centered, node distance=3cm, inner sep=0pt]
\tikzstyle{block} = [rectangle, draw, fill=blue!20, 
    text width=5em, text centered, rounded corners, minimum height=2em, node distance=2cm]
\tikzstyle{block8} = [rectangle, draw, fill=blue!7, 
text width=5em, text centered, rounded corners, minimum height=2em, node distance=2cm, minimum width=8cm]
\tikzstyle{bigblock10} = [rectangle, draw, fill=red!20, 
	text width=5em, text centered, rounded corners, minimum height=4em, minimum width=10cm]
\tikzstyle{line} = [draw, -latex']
\tikzstyle{cloud} = [draw, ellipse,fill=red!20, node distance=3cm,
    minimum height=2em]

\begin{tikzpicture}[node distance = 2cm, auto]
	\node [bigblock10] (bert) at (0,0) {bert model};
	\node [block, below of=bert] (SEP1) {'SEP'};
	\node [block, left of=SEP1] (question) {question};
	\node [block, left of=question] (CLS) {'CLS'};
	\node [block, right of=SEP1] (answer) {answer};
	\node [block, right of=answer] (SEP2) {'SEP'};
	\node [block] (classifier) at (-4,2) {classifier token};
	\node [block8] (rest) at (1,2) {unused tokens};
    \path [line] (CLS) -- ([xshift=-4cm]bert.south);
    \path [line] (question) -- ([xshift=-2cm]bert.south);
    \path [line] (SEP1) -- (bert.south);
    \path [line] (answer) -- ([xshift=2cm]bert.south);
    \path [line] (SEP2) -- ([xshift=4cm]bert.south);
    \path [line] ([xshift=-4cm]bert.north) -- (classifier.south);

    \path [line,dashed] ([xshift=-2cm]bert.north) -- ([xshift=-3cm]rest.south);
    \path [line,dashed] ([xshift=-0cm]bert.north) -- ([xshift=-1cm]rest.south);
    \path [line,dashed] ([xshift=2cm]bert.north) -- ([xshift=1cm]rest.south);
    \path [line,dashed] ([xshift=4cm]bert.north) -- ([xshift=3cm]rest.south);

\end{tikzpicture}

\end{document}

### 2019-08-05 paper/paper.tex
Added original paper diagram
adding a paragraph and the paper current pdf file

@@
 \usepackage{hyperref}
-
+\usepackage{mathtools}
 % Attempt to make hyperref and algorithmic work together better:
@@
 The main reason for the great success of CWE is that the base model is trained using supervised learning on huge amounts of data, e.g.
-BERT, was trained on 3,300M words.
+BERT, was trained on 3.3B words.
 the fact that CWE models are also self trained makes it easier to collect such huge amount of data without the need to label examples.
-the downside of this models is that they use many parameters (BERT Large - 330M) - so trainig and infering requires large processing power and latency is a challenge for creating real time systems.
+the downside of this models is that they use many parameters (BERT Large - 340M) - so trainig and infering requires large processing power and latency is a challenge for creating real time systems.
 in the next section we will introduce the benchmark model which we aim to improve - BERT for CommonsenseQA (which is identical to BERT for SWAG) as was introduced in the original paper of BERT.
 
-\subsection{BERT benchmark for SWAG}
+\subsection{BERT}
+BERT is a word based CWE model that was pre-trained on two learning objectives.
+given a sentence, predict masked words (15\% of the words were masked) and next sentence prediction.
+BERT’s  model  architecture is a multi-layer bidirectional Transformer encoder \cite{vaswani2017attention} with the following hyper-parameters (BERT Large) - 12 Transformer blocks, hidden size 1024 (H) and 16 self attention heads.
+BERT input can be one or two sentences.
+
+BERT input representation (figure \ref{bert_input_repr}) uses WordPeace \cite{wu2016google} tokenization which is a data driven method that aims to achieve a balance between vocabulary size and out-of-vocab words.
+this way BERT stores only 30K vocabulary words very rarely encounter out-of-vocab words when tokenizing English texts.
+two special token are added for each sentence, a start token [CLS] and an end token [SEP].
+if the input contains two sentences another [CLS] token is added in between the sentences.
+Due to the fact that Transformers do not encode the sequential nature of their inputs a segment ids and position embeddings are added as well to the input.
+
+\begin{figure}[ht]
+\vskip 0.2in
+\begin{center}
+\centerline{\includegraphics[width=\columnwidth]{bert_input_repr}}
+\caption{input representation for BERT (from the original paper).}
+\label{bert_input_repr}
+\end{center}
+\vskip -0.2in
+\end{figure}
+fine tuning BERT is simply swapping out the appropriate input and output, whether the input is a single text or a text pair the input and output pairs are given to the model and the parameters are fine-tuned by back-propagation end to end after connecting to the [CLS] token embedding to a task specific classification layer with a given loss function.
+
+\subsection{BERT baseline for SWAG}
+
+In the BERT Paper, the authors approach the SWAG challange with the following input (input #\ref{original_input_order}).
+that input is fed to BERT architecture and the [CLS] token embedding is used to predict a logit by calculating a dot product with a learned vector.
+this process is done for each answer independently of each other and then a softmax layer with cross entropy loss is calculated to compute the error.
+As we can see, this architecture introduce only H (1024) new parameters to the existing BERT model.
+\begin{equation}
+[CLS][Question][SEP][Answer][SEP] 
+\label{original_input_order}
+\end{equation}
+
+\section{CommonSeneseQA}
+CommonSeneseQA is a dataset which specifically made for common sense reasoning, by asking crowd workers to generate questions from concepts from ConceptNet.
+it contains 12,247 examples and 5 answers per question.
+the Authors use the same architecture as in the BERT benchmark for SWAG
+and report Accuracy score of 56.7\%. The current state of the art
+on this dataset is currently 68.3\% accuracy, 23.6\% below human level.
 
 \section{Methodology}
+We propose a method with different variants to model the dependencies between answers, by feeding answer pairs jointly to BERT's architecture. by doing so, we contribute in different ways:
+
+\begin{itemize}
+
+\item making the model more expressive by removing the independence assumption
+
+\item extending the model to deal with questions as 'what is largest?"
+
+\item  extending the model to deal with answers as 'all answer are correct" or 'none of the above"
+
+\end{itemize}
 
@@
 Simply constructing a matrix with each cell being the score for the matching pair, normalizing each row so that we have a probability matrix, and then calculating the stationary distribution doesn't work well in practice.
-This is because normalizing the matrix causes the model to be unable to understand the absolute value of the scores, e.g.
+This is because normalizing the matrix causes the model to be unable to capture the absolute value of the scores, e.g.
 if it sees a row in which all values are similar, it can't differ the case in which all scores were low (and thus our "current" answer is good) from the case all of the scores were high.

### 2019-08-08 paper/paper.tex
Added figures

--- 2019-08-02 paper/paper.tex
@@
 \usepackage{booktabs} % for professional tables
+\usepackage[latin1]{inputenc}
+\usepackage{tikz}
+
+\usetikzlibrary{shapes,arrows}
+
+% Define block styles
+
+\tikzstyle{block} = [rectangle, draw, fill=blue!20, 
+text width=5em, text centered, rounded corners, minimum height=2em, node distance=2cm]
+\tikzstyle{block8} = [rectangle, draw, fill=blue!7, 
+text width=5em, text centered, rounded corners, minimum height=2em, node distance=2cm, minimum width=8cm]
+\tikzstyle{block10} = [rectangle, draw, fill=blue!7, 
+text width=5em, text centered, rounded corners, minimum height=2em, node distance=2cm, minimum width=10cm]
+\tikzstyle{bigblock10} = [rectangle, draw, fill=red!20, 
+text width=5em, text centered, rounded corners, minimum height=4em, minimum width=10cm]
+\tikzstyle{bigblock14} = [rectangle, draw, fill=red!20, 
+text width=5em, text centered, rounded corners, minimum height=4em, minimum width=14cm]
+\tikzstyle{line} = [draw, -latex']
 
@@
 
-In the original paper, each input sequence consisted of a classifier token ('[CLS]'), the question, a separator token ('[SEP]'), a possible answer, and then another separator token.
+In the original paper, each input sequence consisted of a classifier token ('[CLS]'), the question, a separator token ('[SEP]'), a possible answer, and then another separator token, as seen in figure \ref{fig:model_orig}.
 The classifier token is unique, as the final hidden state corresponding to that token was used as the aggregate sequence representation for the question-answering task.
+
+\tikzset{
+	font={\fontsize{12pt}{12}\selectfont}}
+
+\begin{figure}[h!]
+\begin{center}
+\scalebox{0.7}{
+	\begin{tikzpicture}[node distance = 2cm, auto]
+	\node [bigblock10] (bert) at (0,0) {Pretrained BERT };
+	\node [block, below of=bert] (SEP1) {'SEP'};
+	\node [block, left of=SEP1] (question) {Question};
+	\node [block, left of=question] (CLS) {'CLS'};
+	\node [block, right of=SEP1] (answer) {Answer};
+	\node [block, right of=answer] (SEP2) {'SEP'};
+	\node [block] (classifier) at (-4,2) {Classifier token};
+	\node [block8] (rest) at (1,2) {Unused tokens};
+	\path [line] (CLS) -- ([xshift=-4cm]bert.south);
+	\path [line] (question) -- ([xshift=-2cm]bert.south);
+	\path [line] (SEP1) -- (bert.south);
+	\path [line] (answer) -- ([xshift=2cm]bert.south);
+	\path [line] (SEP2) -- ([xshift=4cm]bert.south);
+	\path [line] ([xshift=-4cm]bert.north) -- (classifier.south);
+
+	\path [line,dashed] ([xshift=-2cm]bert.north) -- ([xshift=-3cm]rest.south);
+	\path [line,dashed] ([xshift=-0cm]bert.north) -- ([xshift=-1cm]rest.south);
+	\path [line,dashed] ([xshift=2cm]bert.north) -- ([xshift=1cm]rest.south);
+	\path [line,dashed] ([xshift=4cm]bert.north) -- ([xshift=3cm]rest.south);
+
+	\end{tikzpicture}
+}
+\end{center}
+\caption{The original paper's question-answering model.}
+\label{fig:model_orig}
+\end{figure}
+
 Our model deviates from these assumptions.
-Instead, each input sequence was constructed from the question and 2 possible answers in the following manner: A classifier token, the first answer, a separator token, the question, a separator token, the second answer, and another classifier token.
+Instead, each input sequence was constructed from the question and 2 possible answers in the following manner: A classifier token, the first answer, a separator token, the question, a separator token, the second answer, and another classifier token (As seen in figure \ref{fig:model}).
 Note, that this construction break several of the original BERT paper assumptions - each of our input sequences consist of more than just one classifier token, and more than just two sentences.
@@
 However, breaking these assumptions was a crucial part of what made our constructions work - it allowed for each of the classifier tokens to "absorb" the meaning of the answer closer to it, and imporved the symmetry of our model in regard to each of the two answers.
+
+\tikzset{
+	font={\fontsize{13pt}{14}\selectfont}}
+
+\begin{figure}[h!]
+\begin{center}
+	\scalebox{0.6}{
+		\begin{tikzpicture}[node distance = 2cm, auto]
+		\node [bigblock14] (bert) at (0,0) {Pretrained BERT};
+		\node [block, below of=bert] (Question) {Question};
+		\node [block, left of=Question] (Sep1) {'SEP'};
+		\node [block, left of=Sep1] (Answer1) {Answer1};
+		\node [block, left of=Answer1] (Cls1) {'CLS'};
+		\node [block, right of=Question] (Sep2) {'SEP'};
+		\node [block, right of=Sep2] (Answer2) {Answer2};
+		\node [block, right of=Answer2] (Cls2) {'CLS'};
+		\node [block] (classifier1) at (-6,2) {Classifier token 1};
+		\node [block] (classifier2) at (6,2) {Classifier token 2};
+		\node [block10] (rest) at (0,2) {Unused tokens};
+
+		\path [line] (Cls1) -- ([xshift=-6cm]bert.south);
+		\path [line] (Answer1) -- ([xshift=-4cm]bert.south);
+		\path [line] (Sep1) -- ([xshift=-2cm]bert.south);
+		\path [line] (Question) -- (bert.south);
+		\path [line] (Sep2) -- ([xshift=2cm]bert.south);
+		\path [line] (Answer2) -- ([xshift=4cm]bert.south);
+		\path [line] (Cls2) -- ([xshift=6cm]bert.south);
+
+		\path [line] ([xshift=-6cm]bert.north) -- (classifier1.south);
+		\path [line] ([xshift=6cm]bert.north) -- (classifier2.south);
+
+		\path [line,dashed] ([xshift=-4cm]bert.north) -- ([xshift=-4cm]rest.south);
+		\path [line,dashed] ([xshift=-2cm]bert.north) -- ([xshift=-2cm]rest.south);
+		\path [line,dashed] ([xshift=-0cm]bert.north) -- ([xshift=-0cm]rest.south);
+		\path [line,dashed] ([xshift=2cm]bert.north) -- ([xshift=2cm]rest.south);
+		\path [line,dashed] ([xshift=4cm]bert.north) -- ([xshift=4cm]rest.south);
+		\end{tikzpicture}
+	}
+\end{center}
+\caption{Our question-answering model.}
+\label{fig:model}
+\end{figure}
 

### 2019-08-08 paper/paper.tex
Added experiment results

@@
 Our models were trained in parts.
-In the first part, we trained solely on the dataset alterations part, without intergrating the pair scores. That is, our model was trained directly on identifying the better answer in a pair
+In the first part, we trained solely on the dataset alterations part, without intergrating the pair scores.
+That is, our model was trained directly on identifying the better answer from a pair of answers.
+After 5 epochs with a dynamic learning rate (starting from 1e-6 and decreasing to 4e-7) we were able to acheive a 70.3\% accuracy on the dev set.
+(Note that this accuracy is measured over pairs and not over questions - it is not comparable to the performance of other models over this dataset).
+
+In the second part, we trained our model for 2 more epochs using each method of pair-scores integration suggested.
+Emperically, using the tie-breakers method on any of the suggested models caused a drop in performance, and thus it was discarded.
+A comparison of our experiment results follows.
+
+\begin{table}[h!]
+	\label{tbl:accuracy}
+	\vskip 0.15in
+	\begin{center}
+		\begin{small}
+			\begin{sc}
+				\begin{tabular}{lr}
+					\toprule
+					Method	& Accuracy (dev-set)\\
+					\midrule
+					Comparative Model + \\ \qquad \qquad Markov chains 	& 49.3\% \\
+					Comparative Model + \\ \qquad \qquad Learnt weights 	& 49.1\% \\
+					\midrule
+					Random guess & 25\% \\
+					Original BERT model & \textbf{56.7\%} \\
+					\bottomrule
+				\end{tabular}
+			\end{sc}
+		\end{small}
+	\end{center}
+	\vskip -0.1in
+	\caption{Partial model accuracy on pairs}
+\end{table}
 

### 2019-08-09 paper/paper.tex
Added equations
Style

--- 2019-08-05 paper/paper.tex
@@
 building a relationship graph between the answers for a given question. 
-then, we compute a centrality measure for each node (answer) in the graph and predict the answer by taking the node with the maximum value of that centrality measure.
+Then, we compute a centrality measure for each node (answer) in the graph and predict the answer by taking the node with the maximum value of that centrality measure.
 We test ourselves on the challenging CommonsenseQA dataset and show that although our method is capable of modeling more complex relationships between the answers we did not manage to improve the current state of the art on this task.
@@
 \section{Introduction}
-When we face a multi-choice question answering (QA) problem where we have to choose the most 
-probable answer we arrive at it with prior information and knowledge. for instance, we have some kind of a
+When we face a multi-choice question answering (QA) problem where we have to choose the most probable answer, we arrive at it with prior information and knowledge. for instance, we have some kind of a
 
-Whereas in some cases the state of the art machine-learning methods which were trained on massive amount of data to infer prediction roles
+% TODO: Complete the previous sentence??
+
+While in some cases the state of the art machine-learning methods which were trained on massive amount of data to infer prediction roles
 outperforms human-level by a large margin (e.g. SQUAD 2.0 \cite{rajpurkar2018know}),
 In the field of common sense reasoning  \cite{talmor2018commonsenseqa} state of the art algorithms fail to generalize and are yet inferior to human level performance.
-this is due to two main reasons.
-first, is that when using algorithms such as fine-tuning a pre-trained language model, it is likely that this knowledge (common sense) does not exist explicitly in the pre training corpus.
-and second, is due to the fact that creating massive datasets for this purpose solely is hard, and developed only in the last years mostly by crowdsourcing.
+This is due to two main reasons: first, is that when using algorithms such as fine-tuning a pre-trained language model, it is likely that this knowledge (common sense) does not exist explicitly in the pre training corpus, and second, is due to the fact that creating massive datasets for this purpose solely is hard, and developed only in the last years mostly by crowdsourcing.
 
-Due to this inherent difficulty of this methods the research community invests resources in creating larger-scale datasets in different difficulty levels, e.g., the SWAG \cite{zellers2018swag} dataset with ~100K examples where \cite{devlin2018bert} demonstrate a model which is already at a human level and the CommonseneQA \cite{talmor2018commonsenseqa} a dataset which was made especially for common sense reasoning with \~{}10K samples where the state of the art is much lower then human-level.
-for a detailed survey of resources see \cite{storks2019commonsense}.
+Due to this inherent difficulty of this task, the research community invests resources in creating larger-scale datasets with different difficulty levels, e.g., the SWAG \cite{zellers2018swag} dataset with ~100K examples for which \cite{devlin2018bert} demonstrate a model which is already at a human level, and the CommonseneQA \cite{talmor2018commonsenseqa}, a dataset which was made especially for common sense reasoning with \~{}10K samples where the state of the art is much lower then human-level.
+For a detailed survey of resources see \cite{storks2019commonsense}.
 
@@
 \section{Background and Related Work}
-Research on machine common sense QA has long been acknowledged for it's critical component in natural language understanding.
-but only recently with the embracing of deep learning in natural language processing and crowdsourcing to create larger scale datasets, major breakthroughs has emerged; to the best of the author's knowledge, the first large scale common sense reasoning QA dataset was introduced is 2018 \cite{storks2019commonsense}.
+Research on machine common sense QA has long been acknowledged for its critical component in natural language understanding.
+However, only recently, with the embracing of deep learning in natural language processing and crowdsourcing to create larger scale datasets, major breakthroughs has emerged; To the best of the author's knowledge, the first large scale common sense reasoning QA dataset was introduced is 2018 \cite{storks2019commonsense}.
 
-Due to the fact that the prominent approach to to solve common sense QA problems is with word embeddings (WE) and contextualized word embeddings (CWE) in the next section we will provide a brief introduction to CVE and explain how to use it in the context of common sense QA.
+Due to the fact that the prominent approach to solve common sense QA problems is with word embeddings (WE) and contextualized word embeddings (CWE) in the next section we will provide a brief introduction to CWE and explain how to use it in the context of common sense QA.
 

### 2019-08-10 paper/paper.tex
Merged changes by Afek

--- 2019-08-08 paper/paper.tex
@@
 The main reason for the great success of CWE is that the base model is trained using supervised learning on huge amounts of data, e.g.
-BERT, was trained on 3,300M words.
+BERT, was trained on 3.3B words.
 the fact that CWE models are also self trained makes it easier to collect such huge amount of data without the need to label examples.
-the downside of this models is that they use many parameters (BERT Large - 330M) - so trainig and infering requires large processing power and latency is a challenge for creating real time systems.
+the downside of this models is that they use many parameters (BERT Large - 340M) - so trainig and infering requires large processing power and latency is a challenge for creating real time systems.
 in the next section we will introduce the benchmark model which we aim to improve - BERT for CommonsenseQA (which is identical to BERT for SWAG) as was introduced in the original paper of BERT.
 
-\subsection{BERT benchmark for SWAG}
+\subsection{BERT}
+BERT is a word based CWE model that was pre-trained on two learning objectives.
+given a sentence, predict masked words (15\% of the words were masked) and next sentence prediction.
+BERT’s  model  architecture is a multi-layer bidirectional Transformer encoder \cite{vaswani2017attention} with the following hyper-parameters (BERT Large) - 12 Transformer blocks, hidden size 1024 (H) and 16 self attention heads.
+BERT input can be one or two sentences.
+
+BERT input representation (figure \ref{bert_input_repr}) uses WordPeace \cite{wu2016google} tokenization which is a data driven method that aims to achieve a balance between vocabulary size and out-of-vocab words.
+this way BERT stores only 30K vocabulary words very rarely encounter out-of-vocab words when tokenizing English texts.
+two special token are added for each sentence, a start token [CLS] and an end token [SEP].
+if the input contains two sentences another [CLS] token is added in between the sentences.
+Due to the fact that Transformers do not encode the sequential nature of their inputs a segment ids and position embeddings are added as well to the input.
+
+\begin{figure}[ht]
+\vskip 0.2in
+\begin{center}
+\centerline{\includegraphics[width=\columnwidth]{bert_input_repr}}
+\caption{input representation for BERT (from the original paper).}
+\label{bert_input_repr}
+\end{center}
+\vskip -0.2in
+\end{figure}
+fine tuning BERT is simply swapping out the appropriate input and output, whether the input is a single text or a text pair the input and output pairs are given to the model and the parameters are fine-tuned by back-propagation end to end after connecting to the [CLS] token embedding to a task specific classification layer with a given loss function.
+
+\subsection{BERT baseline for SWAG}
+
+In the BERT Paper, the authors approach the SWAG challange with the following input (figure \ref{fig:model_orig}).
+that input is fed to BERT architecture and the [CLS] token embedding is used to predict a logit by calculating a dot product with a learned vector.
+this process is done for each answer independently of each other and then a softmax layer with cross entropy loss is calculated to compute the error.
+As we can see, this architecture introduce only H (1024) new parameters to the existing BERT model.
+
+% \begin{equation}
+% [CLS][Question][SEP][Answer][SEP] 
+% \label{original_input_order}
+% \end{equation}
+
+\section{CommonSeneseQA}
+CommonSeneseQA is a dataset which specifically made for common sense reasoning, by asking crowd workers to generate questions from concepts from ConceptNet.
+it contains 12,247 examples and 5 answers per question.
+the Authors use the same architecture as in the BERT benchmark for SWAG
+and report Accuracy score of 56.7\%. The current state of the art
+on this dataset is currently 68.3\% accuracy, 23.6\% below human level.
+
+\section{Methodology}
+We propose a method with different variants to model the dependencies between answers, by feeding answer pairs jointly to BERT's architecture. by doing so, we contribute by:
+\begin{itemize}
+\item making the model more expressive by removing the independence assumption
+\item extending the model to deal with questions as 'what is largest?"
+\item  extending the model to deal with answers as 'all answer are correct" or 'none of the above"
+\end{itemize}
 
@@
 
-We derive our model from the BERT fine-tuning method over multichoice questions, as displayed in the original paper.
+We derive our model from the BERT baseline for SWAG.
 However, as we want our model to compare between the different possible answers, we deviate from the original model by introducing the model with the question and 2 possible answers as each input sequence, for which the model returns a score - 1 meaning the first answer is more likely, and 0 if the second answer is the likeliest.
@@
 
-% TODO: add a diagram displaying our construct and the score calculation (including calculating for (i,j) and (j,i) and averaging with 1-s_(j,i)).
+% $$
+% P := \text{\textit{Learned parameter}}
+% $$
+% $$
+% CT_{i,j} := \text{\textit{Classifier Tokens Concatened}}
+% $$
+% $$
+% S'_{i,j} := P \cdot CT_{i,j}
+% $$
+% $$
+% \text{\textit{Score}}_{i,j} := \frac{S'_{i,j} + (1 - S'_{j,i})}{2}
+% $$
 
-Another part of the input sequence given to BERT is the segment embeddings - a number from {0, 1} which signifies wether the current token is part of the first sentece or the second.
+Another part of the input sequence given to BERT is the segment embeddings - a number from \{0, 1\} which signifies whether the current token is part of the first sentence or the second.
 After trial and error, it was found that we perform best when giving a value of 1 for \textbf{each} of the answer tokens, and 0 for the question tokens.
-That makes sense, as part of the desire for symmetry in our model, and the fact that BERT wasn't trained with a possibilty for a third sentence, so using, for example, the number 2 for our second answer would not make any sense to it.
+That makes sense, as part of the desire for symmetry in our model, and the fact that BERT wasn't trained with a possibility for a third sentence, so using, for example, the number 2 for our second answer would not make any sense to it.
 
 After passing our input sequence through BERT, we use a concatenation of the final hidden states matching the classifier tokens as the sequence representation.
-We learn as a parameter a vector whose dot product with the sequence representation is the score for the given answer pair.
+We learn as a parameter a vector whose dot product with the sequence representation is the score for the given answer pair (equation \ref{edge_score}).
+than, we compute the edge score between answers i to j by 'averaging' the sigmoid result of the two.
+add a sentence \# \ \# \# \# \# \#
+
+\begin{equation}
+  \label{eq:t}
+  \begin{aligned}
+      \vec{CT_{i,j}} &:= \text{\textit{Classifier Tokens Concatenated}}\\ 
+    \vec{P} &:= \text{\textit{Learned parameters}}\\
+    S'_{i,j} &:= sigmoid(\vec{CT_{i,j}} \cdot \vec{P})\\
+    \text{\textit{Score}}_{i,j} &:= \frac{S'_{i,j} + (1-S'_{j,i}))}{2}
+  \end{aligned}
+  \label{edge_score}
+\end{equation}
 
@@
 the better another answer performed against our current answer, the more likely we are to move to it.
-This process is powerful, because it captures the dependency between the different answers, e.g.
-if answer B is better than answer A, and answer C is better than answer B, than we'd like to factor in that information when comparing between answers A and C.
+This process is powerful, because it captures the dependency between the different answers, e.g. if answer B is better than answer A, and answer C is better than answer B,\# \# \# \# \#
+than we'd like to factor in that information when comparing between answers A and C.
 
@@
 We solve this problem by adding the average of each column to the matching cell on the diagonal.
-This makes sense, as this gives us the option of staying on the current choice, and the better a certain choice had performed against the other choices, the greater the possibilty of staying on it.
+This makes sense, as this gives us the option of staying on the current choice, and the better a certain choice had performed against the other choices, the greater the possibility of staying on it.
 After doing this, we derive this matrix for our example:
@@
 
-As our model deviates greatly from the assumptions that were made when the original BERT weights were trained, it is understanable that our model required more epochs to converge than the amount of epochs the original paper used when fine-tuning to the question answering task.
+As our model deviates greatly from the assumptions that were made when the original BERT weights were trained, it is understandable that our model required more epochs to converge than the amount of epochs the original paper used when fine-tuning to the question answering task.
 We should also note that because each sample now consists of much more input sequences (the original model had one sequence per possible answer, our model has one sequence per possible answer \textbf{pair}), we are now more limited in our batch size, as the GPU has to hold the entire batch simultaneously.
@@
 Our models were trained in parts.
-In the first part, we trained solely on the dataset alterations part, without intergrating the pair scores.
+In the first part, we trained solely on the dataset alterations part, without integrating the pair scores.
 That is, our model was trained directly on identifying the better answer from a pair of answers.
-After 5 epochs with a dynamic learning rate (starting from 1e-6 and decreasing to 4e-7) we were able to acheive a 70.3\% accuracy on the dev set.
+After 5 epochs with a dynamic learning rate (starting from 1e-6 and decreasing to 4e-7) we were able to achieve a 70.3\% accuracy on the dev set.
 (Note that this accuracy is measured over pairs and not over questions - it is not comparable to the performance of other models over this dataset).
@@
 In the second part, we trained our model for 2 more epochs using each method of pair-scores integration suggested.
-Emperically, using the tie-breakers method on any of the suggested models caused a drop in performance, and thus it was discarded.
+Empirically, using the tie-breakers method on any of the suggested models caused a drop in performance, and thus it was discarded.
 A comparison of our experiment results follows.
@@
 					Random guess & 25\% \\
-					Original BERT model & \textbf{56.7\%} \\
+					Original BERT model (baseline) & \textbf{56.7\%} \\
 					\bottomrule
@@
 	\vskip -0.1in
-	\caption{Partial model accuracy on pairs}
+	\caption{Full model comparison}
 \end{table}
 
-\section{Stuff from the example paper}
+\section{Discussion}
+\subsection{Train-Test Discrepancy}
+when humans tackle multi-choice questions we compare all answer pairs simultaneously, disqualify some unreasonable answers and approve others before we make a prediction.
+those, we narrow the number of possible solutions in a multi-phase process.
+in this paper, this is exactly what we wanted to achieve when we compared all answers pairs altogether.
+we believe that our model under performed because of Train Test Discrepancy; we are aiming to learn in a supervised way information which is not exactly given to us - in the training set, we know only the gold labels per each question and not the relationship between them.
+therefore, there is no information about answers which are totally wrong or answers which are close to each other and can be the prediction candidates.
 
-Submission cite{TechReport} to ICML 2019 will be entirely electronic, via a web site
-(not email). Information about the submission process and \LaTeX\ templates
-are available on the conference web site at:
-\begin{center}
-\textbf{\texttt{http://icml.cc/}}
-\end{center}
+as well, in the training phase we create 4 answer pairs - the gold answer with all the other answers (number of answers - 1) and at test time we create all possible answer pairs which is 20.
+it appears that at training time the model learns to discriminate between the right answer and the wrong answer.
+a dynamic which is not necessarily the same at test time when we feed all answer pairs together.
+this discrepancy can be inherent in the dataset and the way it was built.
+e.g , it may be that the gold answer is better then all the other candidate answer but some answers are distractors which ``confuse" the model at test time.
 
-The guidelines below will be enforced for initial submissions and
-camera-ready copies. Here is a brief summary:
+\subsection{Conclusions}
+Neither the Markovian model nor the Learnt weights model outperformed the baseline model, in fact there was a siginficant gap between our methods and the baseline results.
+we believe that it is due to a combination of the following reasons:
 \begin{itemize}
-\item Submissions must be in PDF\@.
-\item Submitted papers can be up to eight pages long, not including references, and up to twelve pages when references and acknowledgments are included.
-Any paper exceeding this length will automatically be rejected.
-\item \textbf{Do not include author information or acknowledgements} in your
-    initial submission.
-\item Your paper should be in \textbf{10 point Times font}.
-\item Make sure your PDF file only uses Type-1 fonts.
-\item Place figure captions \emph{under} the figure (and omit titles from inside
-    the graphic file itself). Place table captions \emph{over} the table.
-\item References must include page numbers whenever possible and be as complete
-    as possible. Place multiple citations in chronological order.
-\item Do not alter the style template; in particular, do not compress the paper
-    format by reducing the vertical spaces.
-\item Keep your abstract brief and self-contained, one paragraph and roughly
-    4--6 sentences. Gross violations will require correction at the
-    camera-ready phase. The title should have content words capitalized.
+\item train-test discrepancy issue.
+\item BERT was trained in a different manner than our architecture.
+it is likely  that our input representation has harmed the information distillation from the original BERT model those harming the final result.
+it is still an open question which input configuration is optimal in the sense that information from BERT model is kept but also answer pair information is learned.
+\item  bigger datasets can help in this manner in order to be able to generalize well input configurations that is different then BERT baseline.
+as well, bigger datasets  can allow more freedom to use larger models with more parameters.
+in the current model we have 5 samples per each parameter learned which requires large regularization, possibly more complex generalization rules.
 \end{itemize}
 
-\subsection{Submitting Papers}
+\section{Future Work}
+To solve the train-test discrepancy issue, we believe that it is possible to create a dataset with more detailed training labels, for example, ranking the answers and providing information about distractor answers.
+it is interesting to verify if we can achieve a better performance by removing this discrepancy.
 
-\textbf{Paper Deadline:} The deadline for paper submission that is
-advertised on the conference website is strict. If your full,
-anonymized, submission does not reach us on time, it will not be
-considered for publication.
-
-\textbf{Anonymous Submission:} ICML uses double-blind review: no identifying
-author information may appear on the title page or in the paper
-itself. Section~\ref{author info} gives further details.
-
-\textbf{Simultaneous Submission:} ICML will not accept any paper which,
-at the time of submission, is under review for another conference or
-has already been published. This policy also applies to papers that
-overlap substantially in technical content with conference papers
-under review or previously published. ICML submissions must not be
-submitted to other conferences during ICML's review period. Authors
-may submit to ICML substantially different versions of journal papers
-that are currently under review by the journal, but not yet accepted
-at the time of submission. Informal publications, such as technical
-reports or papers in workshop proceedings which do not appear in
-print, do not fall under these restrictions.
-
-\medskip
-
-Authors must provide their manuscripts in \textbf{PDF} format.
-Furthermore, please make sure that files contain only embedded Type-1 fonts
-(e.g.,~using the program \texttt{pdffonts} in linux or using
-File/DocumentProperties/Fonts in Acrobat). Other fonts (like Type-3)
-might come from graphics files imported into the document.
-
-Authors using \textbf{Word} must convert their document to PDF\@. Most
-of the latest versions of Word have the facility to do this
-automatically. Submissions will not be accepted in Word format or any
-format other than PDF\@. Really. We're not joking. Don't send Word.
-
-Those who use \textbf{\LaTeX} should avoid including Type-3 fonts.
-Those using \texttt{latex} and \texttt{dvips} may need the following
-two commands:
-
-{\footnotesize
-\begin{verbatim}
-dvips -Ppdf -tletter -G0 -o paper.ps paper.dvi
-ps2pdf paper.ps
-\end{verbatim}}
-It is a zero following the ``-G'', which tells dvips to use
-the config.pdf file. Newer \TeX\ distributions don't always need this
-option.
-
-Using \texttt{pdflatex} rather than \texttt{latex}, often gives better
-results. This program avoids the Type-3 font problem, and supports more
-advanced features in the \texttt{microtype} package.
-
-\textbf{Graphics files} should be a reasonable size, and included from
-an appropriate format. Use vector formats (.eps/.pdf) for plots,
-lossless bitmap formats (.png) for raster graphics with sharp lines, and
-jpeg for photo-like images.
-
-The style file uses the \texttt{hyperref} package to make clickable
-links in documents. If this causes problems for you, add
-\texttt{nohyperref} as one of the options to the \texttt{icml2019}
-usepackage statement.
-
-\subsection{Submitting Final Camera-Ready Copy}
-
-The final versions of papers accepted for publication should follow the
-same format and naming convention as initial submissions, except that
-author information (names and affiliations) should be given. See
-Section~\ref{final author} for formatting instructions.
-
-The footnote, ``Preliminary work. Under review by the International
-Conference on Machine Learning (ICML). Do not distribute.'' must be
-modified to ``\textit{Proceedings of the
-$\mathit{36}^{th}$ International Conference on Machine Learning},
-Long Beach, USA, 2019.
-Copyright 2019 by the author(s).''
-
-For those using the \textbf{\LaTeX} style file, this change (and others) is
-handled automatically by simply changing
-$\mathtt{\backslash usepackage\{icml2019\}}$ to
-$$\mathtt{\backslash usepackage[accepted]\{icml2019\}}$$
-Authors using \textbf{Word} must edit the
-footnote on the first page of the document themselves.
-
-Camera-ready copies should have the title of the paper as running head
-on each page except the first one. The running title consists of a
-single line centered above a horizontal rule which is $1$~point thick.
-The running head should be centered, bold and in $9$~point type. The
-rule should be $10$~points above the main text. For those using the
-\textbf{\LaTeX} style file, the original title is automatically set as running
-head using the \texttt{fancyhdr} package which is included in the ICML
-2019 style file package. In case that the original title exceeds the
-size restrictions, a shorter form can be supplied by using
-
-\verb|\icmltitlerunning{...}|
-
-just before $\mathtt{\backslash begin\{document\}}$.
-Authors using \textbf{Word} must edit the header of the document themselves.
-
-\section{Format of the Paper}
-
-All submissions must follow the specified format.
-
-\subsection{Length and Dimensions}
-
-Submitted papers can be up to eight pages long, not including references, and up to twelve pages when references and acknowledgments are included.
-Acknowledgements should be limited to grants and people who contributed to the paper.
-Any submission that exceeds
-this page limit, or that diverges significantly from the specified format,
-will be rejected without review.
-
-The text of the paper should be formatted in two columns, with an
-overall width of 6.75~inches, height of 9.0~inches, and 0.25~inches
-between the columns. The left margin should be 0.75~inches and the top
-margin 1.0~inch (2.54~cm). The right and bottom margins will depend on
-whether you print on US letter or A4 paper, but all final versions
-must be produced for US letter size.
-
-The paper body should be set in 10~point type with a vertical spacing
-of 11~points. Please use Times typeface throughout the text.
-
-\subsection{Title}
-
-The paper title should be set in 14~point bold type and centered
-between two horizontal rules that are 1~point thick, with 1.0~inch
-between the top rule and the top edge of the page. Capitalize the
-first letter of content words and put the rest of the title in lower
-case.
-
-\subsection{Author Information for Submission}
-\label{author info}
-
-ICML uses double-blind review, so author information must not appear. If
-you are using \LaTeX\/ and the \texttt{icml2019.sty} file, use
-\verb+\icmlauthor{...}+ to specify authors and \verb+\icmlaffiliation{...}+ to specify affiliations. (Read the TeX code used to produce this document for an example usage.) The author information
-will not be printed unless \texttt{accepted} is passed as an argument to the
-style file.
-Submissions that include the author information will not
-be reviewed.
-
-\subsubsection{Self-Citations}
-
-If you are citing published papers for which you are an author, refer
-to yourself in the third person. In particular, do not use phrases
-that reveal your identity (e.g., ``in previous work \cite{langley00}, we
-have shown \ldots'').
-
-Do not anonymize citations in the reference section. The only exception are manuscripts that are
-not yet published (e.g., under submission). If you choose to refer to
-such unpublished manuscripts \cite{anonymous}, anonymized copies have
-to be submitted
-as Supplementary Material via CMT\@. However, keep in mind that an ICML
-paper should be self contained and should contain sufficient detail
-for the reviewers to evaluate the work. In particular, reviewers are
-not required to look at the Supplementary Material when writing their
-review.
-
-\subsubsection{Camera-Ready Author Information}
-\label{final author}
-
-If a paper is accepted, a final camera-ready copy must be prepared.
-%
-For camera-ready papers, author information should start 0.3~inches below the
-bottom rule surrounding the title. The authors' names should appear in 10~point
-bold type, in a row, separated by white space, and centered. Author names should
-not be broken across lines. Unbolded superscripted numbers, starting 1, should
-be used to refer to affiliations.
-
-Affiliations should be numbered in the order of appearance. A single footnote
-block of text should be used to list all the affiliations. (Academic
-affiliations should list Department, University, City, State/Region, Country.
-Similarly for industrial affiliations.)
-
-Each distinct affiliations should be listed once. If an author has multiple
-affiliations, multiple superscripts should be placed after the name, separated
-by thin spaces. If the authors would like to highlight equal contribution by
-multiple first authors, those authors should have an asterisk placed after their
-name in superscript, and the term ``\textsuperscript{*}Equal contribution"
-should be placed in the footnote block ahead of the list of affiliations. A
-list of corresponding authors and their emails (in the format Full Name
-\textless{}email@domain.com\textgreater{}) can follow the list of affiliations.
-Ideally only one or two names should be listed.
-
-A sample file with author names is included in the ICML2019 style file
-package. Turn on the \texttt{[accepted]} option to the stylefile to
-see the names rendered. All of the guidelines above are implemented
-by the \LaTeX\ style file.
-
-\subsection{Abstract}
-
-The paper abstract should begin in the left column, 0.4~inches below the final
-address. The heading `Abstract' should be centered, bold, and in 11~point type.
-The abstract body should use 10~point type, with a vertical spacing of
-11~points, and should be indented 0.25~inches more than normal on left-hand and
-right-hand margins. Insert 0.4~inches of blank space after the body. Keep your
-abstract brief and self-contained, limiting it to one paragraph and roughly 4--6
-sentences. Gross violations will require correction at the camera-ready phase.
-
-\subsection{Partitioning the Text}
-
-You should organize your paper into sections and paragraphs to help
-readers place a structure on the material and understand its
-contributions.
-
-\subsubsection{Sections and Subsections}
-
-Section headings should be numbered, flush left, and set in 11~pt bold
-type with the content words capitalized. Leave 0.25~inches of space
-before the heading and 0.15~inches after the heading.
-
-Similarly, subsection headings should be numbered, flush left, and set
-in 10~pt bold type with the content words capitalized. Leave
-0.2~inches of space before the heading and 0.13~inches afterward.
-
-Finally, subsubsection headings should be numbered, flush left, and
-set in 10~pt small caps with the content words capitalized. Leave
-0.18~inches of space before the heading and 0.1~inches after the
-heading.
-
-Please use no more than three levels of headings.
-
-\subsubsection{Paragraphs and Footnotes}
-
-Within each section or subsection, you should further partition the
-paper into paragraphs. Do not indent the first line of a given
-paragraph, but insert a blank line between succeeding ones.
-
-You can use footnotes\footnote{Footnotes
-should be complete sentences.} to provide readers with additional
-information about a topic without interrupting the flow of the paper.
-Indicate footnotes with a number in the text where the point is most
-relevant. Place the footnote in 9~point type at the bottom of the
-column in which it appears. Precede the first footnote in a column
-with a horizontal rule of 0.8~inches.\footnote{Multiple footnotes can
-appear in each column, in the same order as they appear in the text,
-but spread them across columns and pages if possible.}
-
-\begin{figure}[ht]
-\vskip 0.2in
-\begin{center}
-\centerline{\includegraphics[width=\columnwidth]{icml_numpapers}}
-\caption{Historical locations and number of accepted papers for International
-Machine Learning Conferences (ICML 1993 -- ICML 2008) and International
-Workshops on Machine Learning (ML 1988 -- ML 1992). At the time this figure was
-produced, the number of accepted papers for ICML 2008 was unknown and instead
-estimated.}
-\label{icml-historical}
-\end{center}
-\vskip -0.2in
-\end{figure}
-
-\subsection{Figures}
-
-You may want to include figures in the paper to illustrate
-your approach and results. Such artwork should be centered,
-legible, and separated from the text. Lines should be dark and at
-least 0.5~points thick for purposes of reproduction, and text should
-not appear on a gray background.
-
-Label all distinct components of each figure. If the figure takes the
-form of a graph, then give a name for each axis and include a legend
-that briefly describes each curve. Do not include a title inside the
-figure; instead, the caption should serve this function.
-
-Number figures sequentially, placing the figure number and caption
-\emph{after} the graphics, with at least 0.1~inches of space before
-the caption and 0.1~inches after it, as in
-Figure~\ref{icml-historical}. The figure caption should be set in
-9~point type and centered unless it runs two or more lines, in which
-case it should be flush left. You may float figures to the top or
-bottom of a column, and you may set wide figures across both columns
-(use the environment \texttt{figure*} in \LaTeX). Always place
-two-column figures at the top or bottom of the page.
-
-\subsection{Algorithms}
-
-If you are using \LaTeX, please use the ``algorithm'' and ``algorithmic''
-environments to format pseudocode. These require
-the corresponding stylefiles, algorithm.sty and
-algorithmic.sty, which are supplied with this package.
-Algorithm~\ref{alg:example} shows an example.
-
-\begin{algorithm}[tb]
-   \caption{Bubble Sort}
-   \label{alg:example}
-\begin{algorithmic}
-   \STATE {\bfseries Input:} data $x_i$, size $m$
-   \REPEAT
-   \STATE Initialize $noChange = true$.
-   \FOR{$i=1$ {\bfseries to} $m-1$}
-   \IF{$x_i > x_{i+1}$}
-   \STATE Swap $x_i$ and $x_{i+1}$
-   \STATE $noChange = false$
-   \ENDIF
-   \ENDFOR
-   \UNTIL{$noChange$ is $true$}
-\end{algorithmic}
-\end{algorithm}
-
-\subsection{Tables}
-
-You may also want to include tables that summarize material. Like
-figures, these should be centered, legible, and numbered consecutively.
-However, place the title \emph{above} the table with at least
-0.1~inches of space before the title and the same after it, as in
-Table~\ref{sample-table}. The table title should be set in 9~point
-type and centered unless it runs two or more lines, in which case it
-should be flush left.
-
-% Note use of \abovespace and \belowspace to get reasonable spacing
-% above and below tabular lines.
-
-\begin{table}[t]
-\caption{Classification accuracies for naive Bayes and flexible
-Bayes on various data sets.}
-\label{sample-table}
-\vskip 0.15in
-\begin{center}
-\begin{small}
-\begin{sc}
-\begin{tabular}{lcccr}
-\toprule
-Data set & Naive & Flexible & Better? \\
-\midrule
-Breast    & 95.9$\pm$ 0.2& 96.7$\pm$ 0.2& $\surd$ \\
-Cleveland & 83.3$\pm$ 0.6& 80.0$\pm$ 0.6& $\times$\\
-Glass2    & 61.9$\pm$ 1.4& 83.8$\pm$ 0.7& $\surd$ \\
-Credit    & 74.8$\pm$ 0.5& 78.3$\pm$ 0.6&         \\
-Horse     & 73.3$\pm$ 0.9& 69.7$\pm$ 1.0& $\times$\\
-Meta      & 67.1$\pm$ 0.6& 76.5$\pm$ 0.5& $\surd$ \\
-Pima      & 75.1$\pm$ 0.6& 73.9$\pm$ 0.5&         \\
-Vehicle   & 44.9$\pm$ 0.6& 61.5$\pm$ 0.4& $\surd$ \\
-\bottomrule
-\end{tabular}
-\end{sc}
-\end{small}
-\end{center}
-\vskip -0.1in
-\end{table}
-
-Tables contain textual material, whereas figures contain graphical material.
-Specify the contents of each row and column in the table's topmost
-row. Again, you may float tables to a column's top or bottom, and set
-wide tables across both columns. Place two-column tables at the
-top or bottom of the page.
-
-\subsection{Citations and References}
-
-Please use APA reference format regardless of your formatter
-or word processor. If you rely on the \LaTeX\/ bibliographic
-facility, use \texttt{natbib.sty} and \texttt{icml2019.bst}
-included in the style-file package to obtain this format.
-
-Citations within the text should include the authors' last names and
-year. If the authors' names are included in the sentence, place only
-the year in parentheses, for example when referencing Arthur Samuel's
-pioneering work \yrcite{Samuel59}. Otherwise place the entire
-reference in parentheses with the authors and year separated by a
-comma \cite{Samuel59}. List multiple references separated by
-semicolons \cite{kearns89,Samuel59,mitchell80}. Use the `et~al.'
-construct only for citations with three or more authors or after
-listing all authors to a publication in an earlier reference \cite{MachineLearningI}.
-
-Authors should cite their own work in the third person
-in the initial version of their paper submitted for blind review.
-Please refer to Section~\ref{author info} for detailed instructions on how to
-cite your own papers.
-
-Use an unnumbered first-level section heading for the references, and use a
-hanging indent style, with the first line of the reference flush against the
-left margin and subsequent lines indented by 10 points. The references at the
-end of this document give examples for journal articles \cite{Samuel59},
-conference publications \cite{langley00}, book chapters \cite{Newell81}, books
-\cite{DudaHart2nd}, edited volumes \cite{MachineLearningI}, technical reports
-\cite{mitchell80}, and dissertations \cite{kearns89}.
-
-Alphabetize references by the surnames of the first authors, with
-single author entries preceding multiple author entries. Order
-references for the same authors by year of publication, with the
-earliest first. Make sure that each reference includes all relevant
-information (e.g., page numbers).
-
-Please put some effort into making references complete, presentable, and
-consistent. If using bibtex, please protect capital letters of names and
-abbreviations in titles, for example, use \{B\}ayesian or \{L\}ipschitz
-in your .bib file.
-
-\subsection{Software and Data}
-
-We strongly encourage the publication of software and data with the
-camera-ready version of the paper whenever appropriate. This can be
-done by including a URL in the camera-ready copy. However, do not
-include URLs that reveal your institution or identity in your
-submission for review. Instead, provide an anonymous URL or upload
-the material as ``Supplementary Material'' into the CMT reviewing
-system. Note that reviewers are not required to look at this material
-when writing their review.
-
-% Acknowledgements should only appear in the accepted version.
-\section*{Acknowledgements}
-
-\textbf{Do not} include acknowledgements in the initial version of
-the paper submitted for blind review.
-
-If a paper is accepted, the final camera-ready version can (and
-probably should) include acknowledgements. In this case, please
-place such acknowledgements in an unnumbered section at the
-end of the paper. Typically, this will include thanks to reviewers
-who gave useful comments, to colleagues who contributed to the ideas,
-and to funding agencies and corporate sponsors that provided financial
-support.
+Another interesting idea to do with a ranked dataset is to fully ``neuralize"" our Markov chain solution.
+one way to do that can be by feeding all the answer pairs jointly to  BERT, compute a logit to every pair and compare it with the ranked ground troth ,than use a graph convolutional layers to classify the correct answer.
+it can also be interesting to examine the graph layer of this network for explainability reasons.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\appendix
-\section{Do \emph{not} have an appendix here}
-
-\textbf{\emph{Do not put content after the references.}}
-%
-Put anything that you might normally include after the references in a separate
-supplementary file.
-
-We recommend that you build supplementary material in a separate document.
-If you must create one PDF and cut it up, please be careful to use a tool that
-doesn't alter the margins, and that doesn't aggressively rewrite the PDF file.
-pdftk usually works fine.
-
-\textbf{Please do not use Apple's preview to cut off supplementary material.} In
-previous years it has altered margins, and created headaches at the camera-ready
-stage. 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-08-10 paper/paper.tex
Style changes, added markov chain

@@
 
-\usetikzlibrary{shapes,arrows}
+\usetikzlibrary{shapes,automata,arrows,positioning,calc}
 
@@
 \subsection{Contextualized Word Embeddings}
-Based on the pioneering work of Word2Vec \cite{mikolov2013distributed} which enabled words to be represented as vectors, those
+Based on the pioneering work of Word2Vec \cite{mikolov2013distributed} which enabled words to be represented as vectors, thus
 enriching the information contained in the input for a variation of language based machine learning tasks, many models extended the Word2Vec concept by taking context into account; the same word has a different meaning in different context.
-the leading approaches to obtain a contextualized word representations is using the hidden layer of an LSTM \cite{hochreiter1997long} and more specifically a biLSTM such as in ELMO \cite{peters2018deep} or more recently using a transformer architecture such as \cite{devlin2018bert,yang2019xlnet}.
+The leading approaches to obtain a contextualized word representations is using the hidden layer of an LSTM \cite{hochreiter1997long} and more specifically a Bi-LSTM such as in ELMO \cite{peters2018deep} or more recently using a transformer architecture such as BERT \cite{devlin2018bert,yang2019xlnet}.
 
-The great power of WE or CWE is to enable using a generic method as a basis for task specific machine learning models; for instance, in natural language processing there are many different tasks (e.g.
-machine translation, sentiment analysis) and a simple model based on CWE with fine tuning on a given dataset usually provides much better results than previous models on a given task, creating a new bencmark for this specific task.
-the fact that mega companies provides those trained models as an open source service makes it easy to use for academics and in the industry as one.
+The great power of WE or CWE is to enable using a generic method as a basis for task specific machine learning models; For instance, in the field of natural language processing there are many different tasks (e.g.
+machine translation, sentiment analysis), yet a simple model based on CWE with fine tuning on a given dataset usually provides much better results than previous models on a given task, creating a new benchmark for this specific task.
+Companies interested in the field of natural language processing often release those trained models as an open source service, which makes CWE easy to use for academics and in the industry as one.
 
-CWE is a type of transfer learning method; a model is pretrained on a base dataset and fine tuned on the task dataset,  with the underlying hypothesis that information distilation is possible from one source (base dataset) to the other (task specific dataset).
+CWE is a type of a transfer learning method; a model is pretrained on a base dataset and fine tuned on the specific task dataset,  with the underlying assumption that information distillation is possible from one source (base dataset) to the other (task specific dataset).
 The main reason for the great success of CWE is that the base model is trained using supervised learning on huge amounts of data, e.g.
 BERT, was trained on 3.3B words.
-the fact that CWE models are also self trained makes it easier to collect such huge amount of data without the need to label examples.
-the downside of this models is that they use many parameters (BERT Large - 340M) - so trainig and infering requires large processing power and latency is a challenge for creating real time systems.
-in the next section we will introduce the benchmark model which we aim to improve - BERT for CommonsenseQA (which is identical to BERT for SWAG) as was introduced in the original paper of BERT.
+The fact that CWE models are also self trained makes it easier to collect such huge amount of data without the need to label samples.
+The downside of these models is that they use many parameters (BERT Large - 340M) - so much such that training and infering requires large processing power and latency is a challenge for creating real time systems.
+In the next section we will introduce the benchmark model which we aim to improve - BERT for CommonsenseQA (which is identical to BERT for SWAG) as was introduced in the original paper of BERT.
 
 \subsection{BERT}
-BERT is a word based CWE model that was pre-trained on two learning objectives.
-given a sentence, predict masked words (15\% of the words were masked) and next sentence prediction.
-BERT’s  model  architecture is a multi-layer bidirectional Transformer encoder \cite{vaswani2017attention} with the following hyper-parameters (BERT Large) - 12 Transformer blocks, hidden size 1024 (H) and 16 self attention heads.
-BERT input can be one or two sentences.
+BERT is a word based CWE model that was pre-trained on two learning objectives: Masked word predictions (15\% of the words were masked) and next sentence predictions.
+BERT's model  architecture is a multi-layer bidirectional Transformer encoder \cite{vaswani2017attention} with the following hyper-parameters (BERT Large) - 12 Transformer blocks, hidden size 1024 (H) and 16 self attention heads.
+BERT takes as input one or two sentences.
 
-BERT input representation (figure \ref{bert_input_repr}) uses WordPeace \cite{wu2016google} tokenization which is a data driven method that aims to achieve a balance between vocabulary size and out-of-vocab words.
-this way BERT stores only 30K vocabulary words very rarely encounter out-of-vocab words when tokenizing English texts.
-two special token are added for each sentence, a start token [CLS] and an end token [SEP].
-if the input contains two sentences another [CLS] token is added in between the sentences.
+BERT's input representation (figure \ref{bert_input_repr}) uses WordPeace \cite{wu2016google} tokenization which is a data driven method that aims to achieve a balance between vocabulary size and out-of-vocab words.
+This way BERT stores only 30K vocabulary words, yet very rarely encounters out-of-vocab words when tokenizing English texts.
+Two special token are added for each sentence, a start token [CLS] and an end token [SEP].
+If the input contains two sentences another [SEP] token is added in between the sentences.
 Due to the fact that Transformers do not encode the sequential nature of their inputs a segment ids and position embeddings are added as well to the input.
 
-\begin{figure}[ht]
+\begin{figure}[h!]
 \vskip 0.2in
@@
 \end{figure}
-fine tuning BERT is simply swapping out the appropriate input and output, whether the input is a single text or a text pair the input and output pairs are given to the model and the parameters are fine-tuned by back-propagation end to end after connecting to the [CLS] token embedding to a task specific classification layer with a given loss function.
+
+Fine tuning BERT is performed by appending the task specific classification layer with a given loss function to the pretrained model, training using the specific task's input / output, and changing parameters using back-propagation.
 
@@
 
-In the BERT Paper, the authors approach the SWAG challange with the following input (figure \ref{fig:model_orig}).
-that input is fed to BERT architecture and the [CLS] token embedding is used to predict a logit by calculating a dot product with a learned vector.
+In the BERT Paper, the authors approach the SWAG challange with the described input (figure \ref{fig:model_orig}).
+that input is fed to BERT's architecture and the [CLS] token embedding is used to predict a logit by calculating a dot product with a learned vector.
 this process is done for each answer independently of each other and then a softmax layer with cross entropy loss is calculated to compute the error.
-As we can see, this architecture introduce only H (1024) new parameters to the existing BERT model.
-
-% \begin{equation}
-% [CLS][Question][SEP][Answer][SEP] 
-% \label{original_input_order}
-% \end{equation}
-
-\section{CommonSeneseQA}
-CommonSeneseQA is a dataset which specifically made for common sense reasoning, by asking crowd workers to generate questions from concepts from ConceptNet.
-it contains 12,247 examples and 5 answers per question.
-the Authors use the same architecture as in the BERT benchmark for SWAG
-and report Accuracy score of 56.7\%. The current state of the art
-on this dataset is currently 68.3\% accuracy, 23.6\% below human level.
-
-\section{Methodology}
-We propose a method with different variants to model the dependencies between answers, by feeding answer pairs jointly to BERT's architecture. by doing so, we contribute by:
-\begin{itemize}
-\item making the model more expressive by removing the independence assumption
-\item extending the model to deal with questions as 'what is largest?"
-\item  extending the model to deal with answers as 'all answer are correct" or 'none of the above"
-\end{itemize}
-
-\section{Methodology}
-
-We derive our model from the BERT baseline for SWAG.
-However, as we want our model to compare between the different possible answers, we deviate from the original model by introducing the model with the question and 2 possible answers as each input sequence, for which the model returns a score - 1 meaning the first answer is more likely, and 0 if the second answer is the likeliest.
-Having received a score for each of pairs, we then integrate those into probability scores for each of the original answers - and then choose the one with the highest probability as our predicted answer.
-
-\subsection{Dataset alterations}
-
-In the original paper, each input sequence consisted of a classifier token ('[CLS]'), the question, a separator token ('[SEP]'), a possible answer, and then another separator token, as seen in figure \ref{fig:model_orig}.
-The classifier token is unique, as the final hidden state corresponding to that token was used as the aggregate sequence representation for the question-answering task.
-
-\tikzset{
-	font={\fontsize{12pt}{12}\selectfont}}
+As we can see, this architecture introduces only H (1024) new parameters to the existing BERT model.
 
@@
 			\node [bigblock10] (bert) at (0,0) {Pretrained BERT };
-	\node [block, below of=bert] (SEP1) {'SEP'};
+			\node [block, below of=bert] (SEP1) {[SEP]};
 			\node [block, left of=SEP1] (question) {Question};
-	\node [block, left of=question] (CLS) {'CLS'};
+			\node [block, left of=question] (CLS) {[CLS]};
 			\node [block, right of=SEP1] (answer) {Answer};
-	\node [block, right of=answer] (SEP2) {'SEP'};
+			\node [block, right of=answer] (SEP2) {[SEP]};
 			\node [block] (classifier) at (-4,2) {Classifier token};
@@
 
+% \begin{equation}
+% [CLS][Question][SEP][Answer][SEP] 
+% \label{original_input_order}
+% \end{equation}
+
+\section{CommonSeneseQA}
+CommonSenseQA is a dataset specifically made for common sense reasoning, by asking crowd workers to generate questions from concepts from ConceptNet.
+It contains 12,247 examples and 5 answers per question.
+the Authors use the same architecture as in the BERT benchmark for SWAG and report an accuracy score of 56.7\%.
+The current state of the art on this dataset is currently 68.3\% accuracy, which is 23.6\% below human level.
+
+\section{Methodology}
+We propose a method with different variants to model the dependencies between answers, by feeding answer pairs jointly to BERT's architecture. Doing so, we contribute by:
+
+\begin{itemize}
+\item making the model more expressive by removing the independence assumption
+\item extending the model to deal with questions as 'what is largest?"
+\end{itemize}
+
+We derive our model from the BERT baseline for SWAG.
+However, as we want our model to compare between the different possible answers, we deviate from the original model by introducing the model with the question and 2 possible answers as each input sequence, for which the model returns a score - 1 meaning the first answer is more likely, and 0 if the second answer is the likeliest.
+Having received a score for each of pairs, we then integrate those into probability scores for each of the original answers - and then choose the one with the highest probability as our predicted answer.
+
+\subsection{Dataset alterations}
+
+In the original paper, each input sequence consisted of a classifier token ('[CLS]'), the question, a separator token ('[SEP]'), a possible answer, and then another separator token, as seen in figure \ref{fig:model_orig}.
+The classifier token is unique, as the final hidden state corresponding to that token was used as the aggregate sequence representation for the question-answering task.
+
+\tikzset{
+	font={\fontsize{12pt}{12}\selectfont}}
+
 Our model deviates from these assumptions.
 Instead, each input sequence was constructed from the question and 2 possible answers in the following manner: A classifier token, the first answer, a separator token, the question, a separator token, the second answer, and another classifier token (As seen in figure \ref{fig:model}).
-Note, that this construction break several of the original BERT paper assumptions - each of our input sequences consist of more than just one classifier token, and more than just two sentences.
+Note, that this construction breaks several of the original BERT paper assumptions - each of our input sequences consist of more than just one classifier token, and more than just two sentences.
 As such, it is possible that BERT will suffer from reduced performance, as its entire training process was built around these assumptions.
-However, breaking these assumptions was a crucial part of what made our constructions work - it allowed for each of the classifier tokens to "absorb" the meaning of the answer closer to it, and imporved the symmetry of our model in regard to each of the two answers.
+However, breaking these assumptions was a crucial part of what made our constructions work - it allowed for each of the classifier tokens to "absorb" the meaning of the answer closer to it, and imporved the symmetry of our model in regards to each of the two answers.
 
@@
 		\node [block, below of=bert] (Question) {Question};
-		\node [block, left of=Question] (Sep1) {'SEP'};
+		\node [block, left of=Question] (Sep1) {[SEP]};
 		\node [block, left of=Sep1] (Answer1) {Answer1};
-		\node [block, left of=Answer1] (Cls1) {'CLS'};
-		\node [block, right of=Question] (Sep2) {'SEP'};
+		\node [block, left of=Answer1] (Cls1) {[CLS]};
+		\node [block, right of=Question] (Sep2) {[SEP]};
 		\node [block, right of=Sep2] (Answer2) {Answer2};
-		\node [block, right of=Answer2] (Cls2) {'CLS'};
+		\node [block, right of=Answer2] (Cls2) {[CLS]};
 		\node [block] (classifier1) at (-6,2) {Classifier token 1};
@@
 We learn as a parameter a vector whose dot product with the sequence representation is the score for the given answer pair (equation \ref{edge_score}).
-than, we compute the edge score between answers i to j by 'averaging' the sigmoid result of the two.
-add a sentence \# \ \# \# \# \# \#
+Then, we compute the edge score between answers i to j by averaging the sigmoid result of the two.
+
+% TODO: you wrote 'add a sentence', why?
 
 \begin{equation}
-  \label{eq:t}
   \begin{aligned}
-      \vec{CT_{i,j}} &:= \text{\textit{Classifier Tokens Concatenated}}\\ 
+      \vec{CT_{i,j}} &:= \text{\textit{Classifier Tokens Concatenated \footnotemark}}\\ 
     \vec{P} &:= \text{\textit{Learned parameters}}\\
@@
 
+\footnotetext{Classifier tokens concatenated, after running through the BERT model using answers $i, j$ for input}
+
 \subsection{Pair scores integration}
 
-We conceived a few methods of combining the different pair scores into probabilities for the answers. In this section we will review those methods and compare them.
+After runnning the previously described part of the model, we receive a score for each of the answer pairs, meaning "How much more likely is answer A than answer B".
+We conceived a few methods of combining the different pair scores into probabilities for the answers.
+In this section we will review those methods and compare them.
 
@@
 In this method, we introduce more layers to derive the indiviual probabilities from the pair scores.
-We used 2 layers, with a hidden size of $ (number\ of\ pairs)^2 $ and normalizing with a softmax layer.
+We use 2 layers, with a hidden size of $ (number\ of\ pairs)^2 $ and normalizing with a softmax layer.
+This generates a valid probability distribution over the possible answers.
 
@@
 the better another answer performed against our current answer, the more likely we are to move to it.
-This process is powerful, because it captures the dependency between the different answers, e.g. if answer B is better than answer A, and answer C is better than answer B,\# \# \# \# \#
-than we'd like to factor in that information when comparing between answers A and C.
+This process is powerful, because it captures the dependency between the different answers, e.g.
+if answer B is better than answer A, and answer C is better than answer B, then we'd like to factor in that information when comparing between answers A and C.
 
-% TODO: add a markov chain graph here
+\tikzset{
+	font={\fontsize{12pt}{12}\selectfont}}
+
+\begin{figure}[h!]
+	\begin{center}
+		\scalebox{0.6}{
+			\begin{tikzpicture}[->, >=stealth', auto, semithick, node distance=3cm]
+			\tikzstyle{every state}=[fill=white,draw=black,thick,text=black,scale=1]
+			\tikzstyle{every node}=[text=blue]
+			\node[state]    (A)                     {$A$};
+			\node[state]    (B)[above right of=A]   {$B$};
+			\node[state]    (C)[below right of=A]   {$C$};
+			\node[state]    (D)[below right of=B]   {$D$};
+			\path
+			(A) edge[loop left]     node{$0.3$}         (A)
+			edge[bend left]     node{$0.2$}     (B)
+			edge[bend left,below]      node[above=-0.1cm]{$0.45$}      (D)
+			edge[bend right]    node[below=0.3cm]{$0.05$}      (C)
+			(B) edge                node[above=-0.1cm]{$0.1$}           (D)
+			edge[loop above]     node{$0.3$}         (B)
+			edge                node[above=-0.1cm]{$0.05$}           (A)
+			edge[bend right]    node[above=-0.1cm]{$0.55$}           (C)
+			(C) edge                node[above=-0.1cm]{$0.7$}           (D)
+			edge[bend right]    node[above=-0.1cm]{$0.1$}           (B)
+			edge[loop below]     node{$0.05$}         (C)
+			edge                node[above=-0.1cm]{$0.15$}           (A)
+			(D) edge[loop right]    node{$0.55$}     (D)
+			edge[bend right,right]    node{$0$}      (B)
+			edge[bend left]     node{$0.2$}      (C)
+			edge[bend left,above]     node{$0.25$}         (A);
+			\end{tikzpicture}
+		}
+	\end{center}
+	\caption{A markov chain with 4 nodes.}
+	\label{fig:markov_chain}
+\end{figure}
 
@@
 if it sees a row in which all values are similar, it can't differ the case in which all scores were low (and thus our "current" answer is good) from the case all of the scores were high.
-Consider the following matrix:
+Consider the following pair-score matrix, extracted from a sample run of our previously discussed model:
 
@@
 
-We can see that the third answer had won in every comparison - thus, we would expect it to be assigned the highest probability.
+We can see that the third answer had won in every comparison (every non-diagonal cell in the third column is $>0.5$) - thus, we would expect it to be assigned the highest probability.
 Given the currently described method, this in not the case, as the probabilities received would be:
@@
 
-And this probability matrix for our choices:
+We then normalize the matrix and calculate the stationary probability distribution, which now seems to describe the relationships between our answers well:
+
 $$ \begin{bmatrix} 0.16845236 & 0.13252954 & \textbf{0.43521662} & 0.26380148 \end{bmatrix} $$

### 2019-08-10 paper/paper.tex
Style comments for the rest of the paper

@@
 \subsection{Train-Test Discrepancy}
-when humans tackle multi-choice questions we compare all answer pairs simultaneously, disqualify some unreasonable answers and approve others before we make a prediction.
-those, we narrow the number of possible solutions in a multi-phase process.
-in this paper, this is exactly what we wanted to achieve when we compared all answers pairs altogether.
-we believe that our model under performed because of Train Test Discrepancy; we are aiming to learn in a supervised way information which is not exactly given to us - in the training set, we know only the gold labels per each question and not the relationship between them.
-therefore, there is no information about answers which are totally wrong or answers which are close to each other and can be the prediction candidates.
+When humans tackle multi-choice questions we compare all answer pairs simultaneously, disqualify some unreasonable answers and approve others before we make a prediction.
+Thus, we narrow the number of possible solutions in a multi-phase process.
+In this paper, this is exactly what we wanted to achieve when we compared all answers pairs altogether.
+One possible reason for our model's under-performance is Train Test Discrepancy; we are aiming to learn in a supervised way information which is not exactly given to us - In the training set, we know only the gold labels per each question and not the relationship between them.
+Therefore, there is no information about answers which are totally wrong or answers which are close to each other and can be the prediction candidates.
 
-as well, in the training phase we create 4 answer pairs - the gold answer with all the other answers (number of answers - 1) and at test time we create all possible answer pairs which is 20.
-it appears that at training time the model learns to discriminate between the right answer and the wrong answer.
-a dynamic which is not necessarily the same at test time when we feed all answer pairs together.
-this discrepancy can be inherent in the dataset and the way it was built.
-e.g , it may be that the gold answer is better then all the other candidate answer but some answers are distractors which ``confuse" the model at test time.
+Also, assuming we are given 5 possible answers, in the training phase we create 8 answer pairs - the gold answer with all the other answers (for each ordering of the pairs).
+However, at test time we create all possible answer pairs which are 20.
+It appears that at training time the model learns to discriminate between the right answer and the wrong answers, A dynamic which is not necessarily the same at test time when we feed all answer pairs together.
+This discrepancy can be inherent in the dataset and the way it was built, e.g.
+it may be that the gold answer is better then all the other candidate answer but some answers are distractors which "confuse" the model at test time.
 
 \subsection{Conclusions}
-Neither the Markovian model nor the Learnt weights model outperformed the baseline model, in fact there was a siginficant gap between our methods and the baseline results.
-we believe that it is due to a combination of the following reasons:
+Neither the Markovian model nor the Learnt weights model outperformed the baseline model.
+In fact, there was a siginficant gap between our methods and the baseline results.
+We believe that it is due to a combination of the following reasons:
 \begin{itemize}
-\item train-test discrepancy issue.
+\item Train-test discrepancy issue.
 \item BERT was trained in a different manner than our architecture.
-it is likely  that our input representation has harmed the information distillation from the original BERT model those harming the final result.
-it is still an open question which input configuration is optimal in the sense that information from BERT model is kept but also answer pair information is learned.
-\item  bigger datasets can help in this manner in order to be able to generalize well input configurations that is different then BERT baseline.
-as well, bigger datasets  can allow more freedom to use larger models with more parameters.
-in the current model we have 5 samples per each parameter learned which requires large regularization, possibly more complex generalization rules.
+It is likely  that our input representation has harmed the information distillation from the original BERT model thus harming the final result.
+Which input configuration is optimal - is still in open question, in the sense that information from BERT model is distilled but also answer pair information is learnt.
+\item  Bigger datasets can help in this manner, by enabling us to generalize well input configurations that are different than BERT baseline.
 \end{itemize}
@@
 To solve the train-test discrepancy issue, we believe that it is possible to create a dataset with more detailed training labels, for example, ranking the answers and providing information about distractor answers.
-it is interesting to verify if we can achieve a better performance by removing this discrepancy.
+It is interesting to verify if we can achieve a better performance by removing this discrepancy.
 
-Another interesting idea to do with a ranked dataset is to fully ``neuralize"" our Markov chain solution.
-one way to do that can be by feeding all the answer pairs jointly to  BERT, compute a logit to every pair and compare it with the ranked ground troth ,than use a graph convolutional layers to classify the correct answer.
-it can also be interesting to examine the graph layer of this network for explainability reasons.
+Another possible approach to improve upon our work with a \textbf{ranked} dataset is to fully "neuralize" our Markov chain solution.
+For instance, one could create a model that feeds all the answer pairs jointly to  BERT, compute a logit for every pair and compare it with the \textbf{ranked} ground truth, then use convolutional layers to classify the correct answer.
+It can also be interesting to examine the graph layer of this network for explainability reasons.
 

### 2019-08-10 paper/paper.tex
Added full model overview

@@
 Having received a score for each of pairs, we then integrate those into probability scores for each of the original answers - and then choose the one with the highest probability as our predicted answer.
+A full overview of our model can be seen in figure \ref{fig:full_model_overview}.
+
+\tikzset{
+	font={\fontsize{15pt}{14}\selectfont}}
+
+\begin{figure}[h]
+	\begin{center}
+		\scalebox{0.5}{
+			\begin{tikzpicture}[node distance = 2cm, auto]
+			\node (a1) at (0,0) {Answer 1};
+			\node (a2) at (3,0) {Answer 2};
+			\node (a3) at (6,0) {Answer 3};
+			\node (a4) at (9,0) {Answer 4};
+			\node (a5) at (12,0) {Answer 5};
+
+			\node [block] (bert1) at (0,3) {BERT based pair score model};
+			\node [block] (bert2) at (2,3) {BERT based pair score model};
+			\node [block] (bert3) at (4,3) {BERT based pair score model};
+			\node (threedots) at (6,3) {...};
+			\node [block] (bert4) at (8,3) {BERT based pair score model};
+			\node [block] (bert5) at (10,3) {BERT based pair score model};
+			\node [block] (bert6) at (12,3) {BERT based pair score model};
+
+			\path [line] (a1) -- (bert1.south);
+			\path [line] (a2) -- ([xshift=0cm]bert1.south);
+			\path [line] (a1) -- (bert2.south);
+			\path [line] (a3) -- ([xshift=0cm]bert2.south);
+			\path [line] (a1) -- (bert3.south);
+			\path [line] (a4) -- ([xshift=0cm]bert3.south);
+			\path [line] (a2) -- (bert4.south);
+			\path [line] (a5) -- ([xshift=0cm]bert4.south);
+			\path [line] (a3) -- (bert5.south);
+			\path [line] (a5) -- ([xshift=0cm]bert5.south);
+			\path [line] (a4) -- (bert6.south);
+			\path [line] (a5) -- ([xshift=0cm]bert6.south);
+
+			\node [bigblock14, fill=yellow!20,text width=10cm] (integration) at (6,8) {Pair score integration};
+
+			\path [line] (bert1.north) -- node [text width=1.3cm, align=center]{Score for (1,2) pair} ([xshift=-6cm]integration.south);
+			\path [line] (bert2.north) -- node [text width=1.3cm, align=center]{Score for (1,3) pair} ([xshift=-4cm]integration.south);
+			\path [line] (bert3.north) -- node [text width=1.3cm, align=center]{Score for (1,4) pair} ([xshift=-2cm]integration.south);
+			\path [line] (bert4.north) -- node [text width=1.3cm, align=center, xshift=1.7cm]{Score for (2,5) pair} ([xshift=2cm]integration.south);
+			\path [line] (bert5.north) -- node [text width=1.3cm, align=center, xshift=1.7cm]{Score for (3,5) pair} ([xshift=4cm]integration.south);
+			\path [line] (bert6.north) -- node [text width=1.3cm, align=center, xshift=1.7cm]{Score for (4,5) pair} ([xshift=6cm]integration.south);
+
+			\path [line,dashed] ([yshift=0.5cm]threedots.north) -- (integration.south);
+
+			\node [text width=2cm](s1) at (0,11) {Score for answer 1};
+			\node [text width=2cm](s2) at (3,11) {Score for answer 2};
+			\node [text width=2cm](s3) at (6,11) {Score for answer 3};
+			\node [text width=2cm](s4) at (9,11) {Score for answer 4};
+			\node [text width=2cm](s5) at (12,11) {Score for answer 5};
+
+			\path [line] ([xshift=-6cm]integration.north) -- (s1);
+			\path [line] ([xshift=-3cm]integration.north) -- (s2);
+			\path [line] ([xshift=0cm]integration.north) -- (s3);
+			\path [line] ([xshift=3cm]integration.north) -- (s4);
+			\path [line] ([xshift=6cm]integration.north) -- (s5);
+
+			%Leaving some room at the top of the graph
+			\node at (6,12.5){};
+
+			\end{tikzpicture}
+		}
+	\end{center}
+	\caption{Our full model overview.}
+	\label{fig:full_model_overview}
+\end{figure}
 

### 2019-08-10 paper/paper.tex
fixing spelling mistakes, final examination of the paper, added one article to the .bib

@@
 \section{Introduction}
-When we face a multi-choice question answering (QA) problem where we have to choose the most probable answer, we arrive at it with prior information and knowledge. for instance, we have some kind of a
+When we face a multi-choice problem where we have to choose the most 
+probable answer we arrive to it with prior information and knowledge.
+e.g,  example, we have some kind of a language model that tells us if sentence A is more probable then sentence B, and we have knowledge about the physical world which tells us what is more possible or probable.
 
@@
 In the field of common sense reasoning  \cite{talmor2018commonsenseqa} state of the art algorithms fail to generalize and are yet inferior to human level performance.
-This is due to two main reasons: first, is that when using algorithms such as fine-tuning a pre-trained language model, it is likely that this knowledge (common sense) does not exist explicitly in the pre training corpus, and second, is due to the fact that creating massive datasets for this purpose solely is hard, and developed only in the last years mostly by crowdsourcing.
+This is due to two main reasons: first, is that when using algorithms such as fine-tuning a pre-trained language model, it is likely that this knowledge (common sense) does not exist explicitly in the pre-training corpus.
+And second, is due to the fact that creating massive datasets for this purpose solely is hard, and developed only in the last years mostly by crowdsourcing.
 
@@
 
-BERT's input representation (figure \ref{bert_input_repr}) uses WordPeace \cite{wu2016google} tokenization which is a data driven method that aims to achieve a balance between vocabulary size and out-of-vocab words.
-This way BERT stores only 30K vocabulary words, yet very rarely encounters out-of-vocab words when tokenizing English texts.
+BERT's input representation (figure \ref{bert_input_repr}) uses WordPeace \cite{wu2016google} tokenization which is a data driven method that aims to achieve a balance between vocabulary size and out-of-vocabulary words.
+This way BERT stores only 30K vocabulary words, yet very rarely encounters out-of-vocabulary words when tokenizing English texts.
 Two special token are added for each sentence, a start token [CLS] and an end token [SEP].
@@
 \end{figure}
-
-% $$
-% P := \text{\textit{Learned parameter}}
-% $$
-% $$
-% CT_{i,j} := \text{\textit{Classifier Tokens Concatened}}
-% $$
-% $$
-% S'_{i,j} := P \cdot CT_{i,j}
-% $$
-% $$
-% \text{\textit{Score}}_{i,j} := \frac{S'_{i,j} + (1 - S'_{j,i})}{2}
-% $$
 
